### 2025-03-02 contents/abstract.tex
Initial Overleaf Import

\begin{abstract}

% NOT finished

Aim: to write

Methods: to write

Results: to write

Conclusion: to write

\end{abstract}

### 2025-03-02 contents/discussions.tex
Initial Overleaf Import

\section{Discussion and Conclusions}
\label{sec:discu}

% NOT finished.

to write

### 2025-03-02 contents/introduction.tex
Initial Overleaf Import

\section{Introduction}
\label{sec:intro}

% NOT finished

to write

### 2025-03-02 contents/methods.tex
Initial Overleaf Import

\section{Methods}
\label{sec:methods}

% NOT finished

to write

### 2025-03-02 contents/results.tex
Initial Overleaf Import

\section{Results}
\label{sec:results}

% NOT  finished

to write

### 2025-03-02 contents/unofficial_abstract.tex
Initial Overleaf Import

% -*- Mode:TeX -*-

\documentclass{cinc-abstract}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{relsize}
\usepackage{pifont}
\usepackage{currfile}

\newcommand\wordcount{\input{|"texcount -inc -sum -0 -utf8 -ch -template={SUM} \currfilepath"}}

\begin{document}

% The title is set in 14-point Helvetica bold
\title{To write}

% The rest of the title block is set in 12 points Helvetica
\author {Hao Wen, Jingsu Kang\\ % First name, initials and surnames, no ``and''
\ \\ % leave an empty line between authors and affiliation
China Agricultural University\\  % gives affiliation of the first author only
Beijing, China} % city, [state or province,] country only

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTE: The body of the abstract (exclusive of the title, authors, and authors’ affiliations) can be up to 300 words at most
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Aim: to write

Methods: to write

Results: to write

Conclusion: to write

% \ifhandout
% % do nothing
% \else
% \begin{center}
% {\larger[2]\color{red} \ding{43}\ding{43}  Totally \wordcount words \reflectbox{\ding{43}\ding{43}}}
% \end{center}
% \fi

\end{document}

### 2025-03-02 poster.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NIWeek 2014 Poster by T. Reveyrand
% www.microwave.fr
% http://www.microwave.fr/LaTeX.html
% ---------------------------------------
%
% Original template created by:
% Brian Amberg (baposter@brian-amberg.de)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a0paper,portrait]{baposter}

\input{preamble}

\usepackage{textcomp}

\usepackage{hyperref}

\graphicspath{{images/}} % Directory in which figures are stored

 \definecolor{bordercol}{RGB}{40,40,40} % Border color of content boxes
 \definecolor{headercol1}{RGB}{186,215,230} % Background color for the header in the content boxes (left side)
 \definecolor{headercol2}{RGB}{120,120,120} % Background color for the header in the content boxes (right side)
 \definecolor{headerfontcol}{RGB}{0,0,0} % Text color for the header text in the content boxes
 \definecolor{boxcolor}{RGB}{210,235,250} % Background color for the content in the content boxes

\definecolor{jdhblue}{RGB}{2,93,186}

\definecolor{zkblue}{RGB}{88,135,175}
\definecolor{zkbackground}{RGB}{230,232,234}

% \usetikzlibrary{shapes, arrows, external, decorations.pathmorphing, backgrounds, positioning, fit, petri, calc, hobby, cd}

\begin{document}

% \background{ % Set the background to an image (background.pdf)
% \begin{tikzpicture}[remember picture,overlay]
% \draw (current page.north west)+(-2em,2em) node[anchor=north west]
% {\includegraphics[height=1.1\textheight]{images/baposter_background.pdf}};
% \end{tikzpicture}
% }

\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
% boxColorOne=boxcolor, % Background color for the content in the content boxes
boxColorOne=zkbackground,
headershape=roundedright, % Specify the rounded corner in the content box headers
headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
textborder=rectangle,
% background=user,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain
}
%
%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR NAME
%----------------------------------------------------------------------------------------
%
{\includegraphics[scale=0.401]{images/logo_cau_science.png}} % University/lab logo
{
{\bf \fontsize{19pt}{19pt} \selectfont To write}
} % Poster title
{\vspace{0.3em} \smaller Hao WEN$^1$, Jingsu KANG$^2$  \\  % Author names

$^1${\it College of Science, China Agricultural University}\qquad
$^2${\it Tianjin Medical University} \\
\vspace{0.2cm}
{\Large \bf{The George B. Moody PhysioNet Challenge 2025}, ~~~\bf{Team Revenger}}
}
{\includegraphics[scale=0.101]{logo_tmu.jpeg}}

\newif\ifcoloredtext
\coloredtexttrue
\newif\ifboxednn
\boxednntrue

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\headerbox{Introduction}{name=introduction, column=0, row=0, span=3}{
% finished

\begin{itemize}
\item to write
\vspace{-0.2cm}
\item to write
\vspace{-0.2cm}
\item to write
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	Framework
%----------------------------------------------------------------------------------------

\headerbox{The Multi-Stage Framework}{name=framework, column=0, span=3, row=1, below=introduction}{
% finished

\newif\ifFrameworkFigBox
\FrameworkFigBoxfalse

\begin{center}
\input{tikz_plots/multi-stage-framework}
\end{center}

}

%----------------------------------------------------------------------------------------
%	Preprocessing
%----------------------------------------------------------------------------------------

\headerbox{Training Data Preparation}{name=data, column=0, row=1, span=2, below=framework}{
% finished

\begin{itemize}
\item ECG-Image-Kit to generate ECG images from the PTB-XL dataset for our method development. Additionally, the PTB-XL+ dataset was used to generate classification labels.
\vspace{-0.2cm}
\item Image generation setup included augmentations such as random Gaussian noise, random color temperature adjustments, and distortions including handwritten notes, wrinkles, and creases.
\vspace{-0.2cm}
\item Bounding boxes for the printed waveforms and lead names, along with the plotted pixel coordinates of the waveforms, were recorded in metadata files alongside the generated images to train object detection models and segmentation models respectively.
\end{itemize}

}

%----------------------------------------------------------------------------------------
%	Model selection
%----------------------------------------------------------------------------------------

\headerbox{Model Selection}{name=nn, column=2, span=1, row = 2, below=framework}{
% NOT finished

\input{tables/model_select_poster}

Models are chosen based on performance, efficiency, and compatibility with ECG image data.
\newline
\faHandPointRight[regular] DETR: 0.9 mAP \hfill \faHandPointRight[regular] U-Net: 0.73 Dice.
\newline
\faHandPointRight[regular] Total inference time: 2s on single RTX 3090

}

%----------------------------------------------------------------------------------------
%	Novel loss functions
%----------------------------------------------------------------------------------------

\headerbox{Loss Functions}{name=loss, span=2, column=0, below=data}{
% finished

\begin{tikzpicture}
\ImageNode[]{wtmask}{width=0.4\linewidth}{images/weight-mask.pdf}
\node [rectangle, text width = 8.8cm, inner sep = 2pt, minimum height = 1.0em, right=0.3cm of wtmask.north east, anchor=north west] {\faHandPointRight[regular] Segmentation: Since ECG waveforms occupy only a small portion of the image, we used the BCE loss multiplied by a \textbf{\color{red} weight mask} to balance the loss contribution from different parts of the ECG waveforms. The weight mask is the sum of multiple dilations (e.g., dilation iterations 2, 4, 6, and 8) of the binarized ground truth mask. On the left is an example of a weight mask.};
\end{tikzpicture}
\faHandPointRight[regular] Classification: Asymmetric loss $L = -y \cdot (1-p)^{\gamma_{+}} \log(p) - (1-y) \cdot (p_m)^{\gamma_{-}} \log(1-p_m)$
\newline
\faHandPointRight[regular] Object detection: 1 $\times$ bbox class cross-entropy + 5 $\times$ bbox coordinate L1 loss + 2 $\times$ GIoU loss

}

%----------------------------------------------------------------------------------------
%	Submission Results
%----------------------------------------------------------------------------------------

\headerbox{Submission Results}{name=submission, span=1, column=2, below=nn}{
% NOT finished

\begin{center}
\input{tables/final_results_simple}
\end{center}
The rankings are based on the hidden validation set. Results on the public training data (more specifically, the left-out validation set) are also provided for reference.

}

%----------------------------------------------------------------------------------------
%	Limitations, Discussions
%----------------------------------------------------------------------------------------

\headerbox{Discussions and Limitations}{name=discussion, column=0, below=loss, span=3}{
% NOT finished

\begin{itemize}
\item The proposed method is relatively effective in digitizing and classifying ECG images concurrently, achieving an acceptable SNR and F1 score. This multi-stage framework offers a lightweight and efficient solution to this challenge.
\vspace{-0.2cm}
\item There are observable gaps between the SNR metric on the public training data and the hidden validation/test data. A possible reason for this discrepancy is the difference in data distribution (format): training data generated using ECG-Image-Kit all follow the standard 3-by-4 format. The post-processing step after segmentation is designed to handle this specific format. However, the hidden validation/test data may have different formats, e.g. additional full-length waveforms.
\vspace{-0.2cm}
\item Further improvement directions:
\vspace{-0.2cm}
\begin{itemize}
    \item More effective backbone networks or more advanced architectures, including the latest YOLO series models.
    \vspace{-0.1cm}
    \item End-to-end digitization models from the segmented ECG waveform masks or even directly from the ROI can be developed to simplify the pipeline, replacing the current rule-based conversion from pixel coordinates to digitized value.
    \vspace{-0.1cm}
    \item Better handling of rotated ECG images to improve the framework's robustness, using oriented object detection models.
\end{itemize}
\end{itemize}

}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\headerbox{Acknowledgements}{name=acknowledgements, column=0, below=discussion, span=3}{
% finished
% \smaller
We thank professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers to help accomplish this work.

}

%----------------------------------------------------------------------------------------
%	link to the GitHub repository
%----------------------------------------------------------------------------------------

\headerbox{}{name=foottext, column=0, span=3, below=acknowledgements, textborder=none, headerborder=none,  boxheaderheight=0pt}{
% finished
\hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}
}

\end{poster}

\end{document}

### 2025-03-02 compile.py

@@ -1,0 +1,143 @@
+import collections
+import platform
+import shutil
+import subprocess
+import sys
+import time
+from pathlib import Path
+from typing import List, Tuple, Union
+
+project_dir = Path(__file__).resolve().parent
+build_dir = project_dir / "build"
+if not build_dir.exists():
+    build_dir.mkdir(parents=True, exist_ok=True)
+main_tex_file = project_dir / "main.tex"
+
+
+def execute_cmd(cmd: Union[str, List[str]], raise_error: bool = True) -> Tuple[int, List[str]]:
+    """Execute shell command using `Popen`.
+
+    Parameters
+    ----------
+    cmd : str or list of str
+        Shell command to be executed,
+        or a list of .sh files to be executed.
+    raise_error : bool, default True
+        If True, error will be raised when occured.
+
+    Returns
+    -------
+    exitcode : int
+        Exit code returned by `Popen`.
+    output_msg : list of str
+        Outputs from `stdout` of `Popen`.
+
+    """
+    shell_arg, executable_arg = True, None
+    s = subprocess.Popen(
+        cmd,
+        shell=shell_arg,
+        executable=executable_arg,
+        stdout=subprocess.PIPE,
+        stderr=subprocess.STDOUT,
+        close_fds=(not (platform.system().lower() == "windows")),
+    )
+    debug_stdout = collections.deque(maxlen=1000)
+    # print("\n" + "*" * 10 + "  execute_cmd starts  " + "*" * 10 + "\n")
+    while 1:
+        line = s.stdout.readline().decode("utf-8", errors="replace")
+        if line.rstrip():
+            debug_stdout.append(line)
+            print(line)
+        exitcode = s.poll()
+        if exitcode is not None:
+            for line in s.stdout:
+                debug_stdout.append(line.decode("utf-8", errors="replace"))
+            if exitcode is not None and exitcode != 0:
+                error_msg = " ".join(cmd) if not isinstance(cmd, str) else cmd
+                error_msg += "\n"
+                error_msg += "".join(debug_stdout)
+                s.communicate()
+                s.stdout.close()
+                print("\n" + "*" * 10 + "  execute_cmd failed  " + "*" * 10 + "\n")
+                if raise_error:
[…]

### 2025-04-15 contents/unofficial_abstract.tex
finish unofficial phase abstract

@@
 % The title is set in 14-point Helvetica bold
-\title{To write}
+% \title{Hierarchical Learning with Clinical Expertise Integration for Chagas Detection from ECG under Data Scarcity Constraints}
+\title{Hierarchical Learning for Chagas Detection from ECG under Expert-Label Scarcity}
 
@@
 
-Aim: to write
+% Aim: This paper tackles automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), as the George B. Moody PhysioNet Challenge 2025 proposes.
+Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B.
+Moody PhysioNet Challenge 2025.
 
-Methods: to write
+Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance.
+We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive).
+The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported.
+We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones.
+Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability).
+Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence.
+A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.
 
-Results: to write
+Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.
 
-Conclusion: to write
+Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
 

### 2025-08-20 contents/abstract.tex
update official phase abstract

@@
 
-Aim: to write
+Aim: We introduce a reliability‑aware hierarchical learning framework for automated electrocardiogram(ECG)-based Chagas cardiomyopathy screening developed by Team Revenger for the George B.
+Moody PhysioNet Challenge 2025, focusing on maximizing positive case retrieval under low predicted‑prevalence constraints.
 

### 2025-08-21 contents/abstract.tex
finish abtract

--- 2025-03-02 contents/abstract.tex
@@
 
-% NOT finished
+% almost finished
 
-Aim: to write
+% --------------------------------------------------
+% Unofficial phase version:
 
-Methods: to write
+% Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B.
+Moody PhysioNet Challenge 2025.
 
-Results: to write
+% Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance.
+We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive).
+The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported.
+We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones.
+Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability).
+Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence.
+A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.
 
-Conclusion: to write
+% Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.
+
+% Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
+% --------------------------------------------------
+
+Aim: We present a reliability-aware hierarchical learning framework for ECG-based Chagas cardiomyopathy screening in the George B.
+Moody PhysioNet Challenge 2025 by Team Revenger, aiming to maximize positive case retrieval under prevalence constraints.
+
+Methods: The 12-lead ECGs were resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized.
+We used a ResNet architecture model with squeeze-and-excitation (SE) modules for binary classification.
+To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones.
+Model training used an asymmetric loss to further penalize false negatives, optimized with Adam and a OneCycle learning rate schedule.
+Model selection was based on the Challenge score from an internal hold-out subset.
+
+Results: In stratified cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN].
+On the hidden validation set, our method received a Challenge score of [VAL-SCORE] (rank [VAL-RANK]).
+
+Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, offering a promising direction for improving detection accuracy and reliability in resource-limited scenarios.
 

### 2025-08-22 contents/abstract.tex
finish introduction

@@
 Methods: The 12-lead ECGs were resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized.
-We used a ResNet architecture model with squeeze-and-excitation (SE) modules for binary classification.
+We used a ResNet model integrated with squeeze-and-excitation (SE) modules for binary classification.
 To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones.
-Model training used an asymmetric loss to further penalize false negatives, optimized with Adam and a OneCycle learning rate schedule.
+Model training used an asymmetric loss to further penalize false negatives and was optimized with Adam and a OneCycle learning rate schedule.
 Model selection was based on the Challenge score from an internal hold-out subset.
 
-Results: In stratified cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN].
+Results: In cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN].
 On the hidden validation set, our method received a Challenge score of [VAL-SCORE] (rank [VAL-RANK]).
 
-Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, offering a promising direction for improving detection accuracy and reliability in resource-limited scenarios.
+Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.
 

### 2025-08-22 contents/introduction.tex
finish introduction

@@
 
-% NOT finished
+% almost finished
 
-to write
+Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B.
+Moody PhysioNet Challenge \cite{goldberger2000physionet, cinc2025}.
+Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.
+
+In this work, we propose a reliability-aware hierarchical framework that prioritizes expert-confirmed labels and mitigates severe class imbalance within a deep ECG model, with optimization aligned to prevalence-constrained sensitivity objectives.

### 2025-08-23 contents/methods.tex
update official phase abstract
finish introduction
finish subsection Dataset Preparation

@@
 
-to write
+\subsection{Dataset Preparation}
+\label{subsec:data}
+
+% almost finished
+
+We used three ECG datasets for model training, with substantial differences in sample size, Chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.
+
+\begin{table}[!htp]
+\centering
+\begin{tabular}{rlll}
+\toprule
+Dataset & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Chagas rate} & Label provenance \\
+\midrule
+SaMi-Trop & 1\,631   & 100 & expert-confirmed \\
+CODE-15\% & 345\,779 & 1.795   & self-reported \\
+PTB-XL    & 21\,799  & 0   & N/A \\
+\bottomrule
+\end{tabular}
+\caption{Dataset statistics and label provenance.
+Chagas rate is the proportion of recordings labeled positive in each dataset.
+N/A indicates that confirmed Chagas cases are not expected (non-endemic population).}
+\label{tab:dataset_stats}
+\end{table}
+
+All ECGs were uniformly resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized to zero mean and unit variance computed as in Eq.~\ref{eq:z_score}:
+\begin{equation}
+\label{eq:z_score}
+\tilde{\mathbf{x}} = \frac{\mathbf{x} - \boldsymbol{\mu}_x}{\boldsymbol{\sigma}_x}
+\end{equation}
+where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_x$ and $\boldsymbol{\sigma}_x$ are the mean and standard deviation of $\mathbf{x}$, respectively.
+
+To address label reliability, we applied stratified label smoothing \cite{inceptionv2v3}: expert-confirmed positives (SaMi-Trop) use hard labels (smoothing factor $0.0$), self-reported positives (CODE-15\%) use moderate smoothing ($0.6$), and negatives use higher smoothing ($0.2$).
+This reflects greater trust in expert-confirmed labels and accounts for possible noise in other groups.
+Label smoothing is computed according to Eq.~\ref{eq:label_smoothing}:
+\begin{equation}
+\label{eq:label_smoothing}
+\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{K} \cdot \mathbf{1},
+\end{equation}
+where $\mathbf{y}$ is the one-hot ground-truth label ($[0, 1]$ for positives, $[1, 0]$ for negatives), $\varepsilon$ is the smoothing factor, and $\tilde{\mathbf{y}}$ is the smoothed label.
+It should be noted that the smoothing factor $\varepsilon$ varies across samples from different sources.
+
+Severe class imbalance was mitigated by upsampling positives during training: positive samples from CODE-15\% were upsampled by a factor of 3, and those from SaMi-Trop by 7.
+No upsampling was applied to PTB-XL, which contains no positives.
+Smoothed labels and upsampling strategies for each dataset are summarized in Table~\ref{tab:augmentation}.
+
+\begin{table}[!htp]
+\centering
+\begin{tabular}{lcccc}
+\toprule
+\multirow{2}{*}{Dataset} & Upsampling & \multicolumn{2}{c}{Smoothed labels} \\ \cmidrule(lr){3-4}
+& factor & negative & positive \\
+\midrule
+SaMi-Trop & $7$ & N/A           & $[0,\,1]$     \\
+CODE-15\%   & $3$ & $[0.7,\,0.3]$ & $[0.3,\,0.7]$ \\
+PTB-XL    & $1$ & $[0.9,\,0.1]$ & N/A           \\
+\bottomrule
+\end{tabular}
+\caption{Smoothed labels and upsampling strategies for each dataset. Smoothed labels are computed from Eq.~\ref{eq:label_smoothing}.}
+\label{tab:augmentation}
+\end{table}
+
+\subsection{xxx}
+
+% NOT finished
+
+\cite{torch_ecg_paper}

### 2025-08-24 contents/methods.tex
finish methods section

@@
 
-% NOT finished
+% almost finished
 
-\subsection{Dataset Preparation}
+\subsection{Datasets and Preprocessing}
 \label{subsec:data}
@@
 
-We used three ECG datasets for model training, with substantial differences in sample size, Chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.
+We used three ECG datasets for model training, with substantial differences in sample size, chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.
 
@@
 where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_x$ and $\boldsymbol{\sigma}_x$ are the mean and standard deviation of $\mathbf{x}$, respectively.
+We excluded ECGs shorter than 1,200 samples to ensure inputs contain enough cardiac cycles for stable model analysis.
 
-To address label reliability, we applied stratified label smoothing \cite{inceptionv2v3}: expert-confirmed positives (SaMi-Trop) use hard labels (smoothing factor $0.0$), self-reported positives (CODE-15\%) use moderate smoothing ($0.6$), and negatives use higher smoothing ($0.2$).
-This reflects greater trust in expert-confirmed labels and accounts for possible noise in other groups.
-Label smoothing is computed according to Eq.~\ref{eq:label_smoothing}:
+\subsection{Reliability-Aware Hierarchical Supervision}
+\label{subsec:reliability}
+
+% almost finished
+
+We introduce a hierarchical supervision scheme that encodes source reliability through stratified label smoothing and adaptive upsampling.
+Three reliability levels are defined: (1) expert-confirmed positives (SaMi-Trop, maximal trust), (2) self-reported samples (CODE-15\%, both positives and negatives, higher uncertainty), and (3) non-endemic negatives (PTB-XL, very low true prevalence but still mildly regularized).
+Given a one-hot label $\mathbf{y}$ ($[0, 1]$ for positives, $[1, 0]$ for negatives) and number of classes $C = 2,$ the smoothed target is computed as in Eq.~\ref{eq:label_smoothing}:
 \begin{equation}
 \label{eq:label_smoothing}
-\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{K} \cdot \mathbf{1},
+\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1},
 \end{equation}
-where $\mathbf{y}$ is the one-hot ground-truth label ($[0, 1]$ for positives, $[1, 0]$ for negatives), $\varepsilon$ is the smoothing factor, and $\tilde{\mathbf{y}}$ is the smoothed label.
-It should be noted that the smoothing factor $\varepsilon$ varies across samples from different sources.
+where $\varepsilon$ is the smoothing factor which depends on the reliability level: 0.0 (SaMi positives), 0.6 (CODE-15\% positives \& negatives), 0.2 (PTB-XL negatives).
+This attenuates overconfident gradients for noisier or potentially misreported labels while preserving sharp supervision on expert-confirmed cases.
 
@@
 \end{tabular}
-\caption{Smoothed labels and upsampling strategies for each dataset. Smoothed labels are computed from Eq.~\ref{eq:label_smoothing}.}
+\caption{Smoothed labels (computed from Eq.~\ref{eq:label_smoothing}) and upsampling strategies for each dataset.}
 \label{tab:augmentation}
@@
 
-\subsection{xxx}
+\subsection{Model Architecture}
+\label{subsec:model}
 
-% NOT finished
+% almost finished
 
-\cite{torch_ecg_paper}
+We build upon the 1D ResNet ECG classifier of Ribeiro et al.~\cite{ribeiro2020automatic} and introduce three modifications.
+
+\textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of the form $1$–$15$–$1$ (pointwise--temporal--pointwise).
+The middle temporal convolution (kernel size 15) applies stride 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4.
+A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
+Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$,yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.
+
+\textbf{(2) Global squeeze-and-excitation (SE).} After the final bottleneck block, a single global SE module (reduction ratio 8) \cite{hu2018senet} performs temporal average pooling to a channel descriptor, applies a two-layer bottleneck multi-layer perceptron (MLP) $1280 \to 160 \to 1280$ with ReLU and sigmoid gating, and rescales the feature map channel-wise.
+
+\textbf{(3) Global pooling head for variable input length.} Instead of flattening a fixed-length feature map as in the original baseline, we apply global max pooling over the remaining temporal dimension, yielding a 1280-dimensional vector irrespective of input length $L$.
+This vector is fed to a lightweight two-layer classification MLP: a hidden fully connected layer ($1280 \to 1024$) with non-linear activation and dropout (rate 0.2), followed by a final linear layer ($1024 \to 2$) producing class logits.
+
+\textbf{Stem and regularization.} A stem Conv1d (kernel size 15, stride 1, 64 channels) with BatchNorm and ReLU precedes the bottleneck stack.
+Within each bottleneck block we apply BatchNorm+ReLU after the first two convolutions and dropout (rate 0.2) after each of those activations.
+All convolutions use “same” padding to preserve temporal length before downsampling operations.
+
+Overall, the changes primarily enable variable-length inference and add global channel reweighting with minimal structural overhead.
+The resulting model architecture is illustrated in Fig.~\ref{fig:model}.
+
+\begin{figure*}
+\centering
+\input{tikz_plots/resnet_nature_comm_bottle_neck}
+\caption{Model architecture.
+Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
+Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded (post-bottleneck) channels.
+Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
+The middle 15-length convolution uses stride 4 for temporal downsampling; 1$\times$1 convolutions reduce then expand channels, and a projection 1$\times$1 (stride 4) aligns resolution and width for the residual path.
+For clarity, dropout layers present in the implementation are omitted.
+Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
+\label{fig:model}
+\end{figure*}
+
+\subsection{Training and Implementation Setup}
+\label{subsec:train}
+
+% almost finished
+
+We employed an asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to further complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance.
+Let $z$ denote the logits and $p=\sigma(z)$ the predicted probability of the Chagas-positive class, the ASL is defined in Eq.~\ref{eq:asl} with separate focusing parameters for positives and negatives and a clipped negative probability:
+\begin{equation}
+\label{eq:asl}
+\begin{multlined}
+L = -y \cdot (1-p)^{\gamma_{+}} \log(p) \\
+\phantom{L = } - (1-y) \cdot (p_m)^{\gamma_{-}} \log(1-p_m),
+\end{multlined}
+\end{equation}
+where $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $\delta=0.05$.
+We train for 30 epochs with batch size 128 using AdamW (AMSGrad, initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle schedule, weight decay $1\times10^{-2}$).
+Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric.
+Each training segment is a uniform random crop (or center trim if shorter) of length 4,096 samples.
+All components (data pipeline, optimization utilities) are implemented using the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.

### 2025-08-24 preamble.tex
finish methods section

\usepackage[T1]{fontenc}
\usepackage{mathtools, graphicx, xurl, hyperref}
% \usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows.meta, decorations.pathmorphing, decorations.pathreplacing, backgrounds, positioning, fit, calc, shadows, shapes.misc}
% \tikzexternalize[prefix=tikz/,optimize command away=\includepdf]
\usepackage{boldline, multirow}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{colortbl}
\usepackage{subcaption}
\usepackage{relsize}
\usepackage{fontawesome5}
\usepackage[ruled, vlined]{algorithm2e}

\usepackage{tabularx} % for 'X' col. type and 'tabularx' environment
\usepackage{ragged2e} % for '\RaggedRight' macro
\newcolumntype{L}{>{\RaggedRight}X} % disable full justification

% \tikzstyle{smallcircleblock} = [circle, draw, text width = 0.7em, text centered]

% \tikzstyle{wideblock} = [rectangle, draw, text width = 6.5em, text centered, rounded corners, inner sep = 7pt, minimum height = 1.0em]

\newcommand\ImageNode[4][]{
  \node[#1] (#2) {\includegraphics[#3]{#4}};
}
\definecolor{arrowblue}{RGB}{98,145,224}

\newcolumntype{g}{>{\columncolor[gray]{0.8}}l}

\newif\ifcoloredtext
\coloredtextfalse

\newif\ifboxednn
\boxednntrue

\newenvironment{indentedquote}[1]%
{\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
{\endlist}

### 2025-08-24 tikz_plots/resnet_nature_comm_bottle_neck.tex
finish methods section

\begin{tikzpicture}[
    % font=\small,
    line width=0.75pt,
    >={Latex[length=3mm]},
    node distance=6.4mm,
    every node/.style={inner sep=2pt},
    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
                 align=center, fill=blue!10},
    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
                  align=center, fill=orange!12},
    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
               align=center, fill=green!12},
    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
                 align=center, fill=cyan!10},
    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
                 align=center, fill=purple!10},
    output/.style={draw, rounded corners=2pt, minimum width=24mm, minimum height=10mm,
                align=center, fill=red!10},
    arrow/.style={-{Latex[length=3mm]}, thick},
    darr/.style={-{Latex[length=2.4mm]}, thick},
    dashedarrow/.style={-{Latex[length=2.6mm]}, thick, dashed},
    ann/.style={inner sep=1pt, align=center},
    layer/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
                  align=center, fill=blue!6},
    bnact/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
                  align=center, fill=violet!10},
    act/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
                  align=center, fill=red!10},
    drop/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
                  align=center, fill=gray!15, dashed},
    sum/.style={draw, circle, inner sep=1.6pt, fill=white},
    % brace/.style={decorate, decoration={brace, amplitude=6pt}},
    detailbox/.style={draw, rounded corners=3pt, inner sep=6pt, fill=orange!3}
]

% ================= Left (overall vertical path) =================
\node[stem] (input) {Input \\ (12$\times$L)};
\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};

% Compressed single bottleneck block (represents 4 stacked blocks)
\node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1 (stride=4) \\ Ch: $512 \to 768 \to 1024 \to 1280$};

% Global SE
\node[se, below=of bottleneck] (gse) {Global SE \\ reduction=8};

% Global pooling
\node[pool, below=of gse] (gap) {Global MaxPool};

% MLP Head
\node[head, below=of gap] (mlp) {MLP Head \\ (1280 $\rightarrow$ C=2)};

% Output
\node[output, below=of mlp] (out) {Output Logits};

% Arrows (overall path)
\draw[arrow] (input) -- (stem);
\draw[arrow] (stem) -- (bottleneck);
\draw[arrow] (bottleneck) -- (gse);
\draw[arrow] (gse) -- (gap);
\draw[arrow] (gap) -- (mlp);
\draw[arrow] (mlp) -- (out);

% ================= Right (expanded single bottleneck internals) =================
% Anchor for expansion (to the right of overall bottleneck block)
\coordinate (expandAnchor) at ($(input.east)+(45mm,0)$);

\node[layer, below=0mm of expandAnchor] (c1) {Conv 1$\times$1};
\node[below right=-1mm and 8mm of c1.south] {reduce};
\node[bnact, below=5mm of c1] (bn1) {BN};
\node[act, below=5mm of bn1] (a1) {ReLU};

\node[layer, below=5mm of a1] (c2) {Conv 15\\(stride 4)};
\node[bnact, below=5mm of c2] (bn2) {BN};
\node[act, below=5mm of bn2] (a2) {ReLU};
% \node[drop, below=5mm of a2] (drp) {Dropout 0.2};

\node[layer, below=5mm of a2] (c3) {Conv 1$\times$1};
\node[below right=-1mm and 8mm of c3.south] {expand};
\node[bnact, below=5mm of c3] (bn3) {BN};

\node[sum, below=5mm of bn3] (add) {+};
\node[act, below=5mm of add] (outact) {ReLU (output)};

% Projection/skip branch (since stride=4 or channel change)
\node[layer, right=10mm of c2, yshift=-7mm, minimum width=18mm] (proj) {Proj 1$\times$1 \\ (stride 4)};
\node[bnact, below=5mm of proj, minimum width=18mm] (projbn) {BN};

% Connections internal
\draw[darr] (c1) -- (bn1);
\draw[darr] (bn1) -- (a1);
\draw[darr] (a1) -- (c2);
\draw[darr] (c2) -- (bn2);
\draw[darr] (bn2) -- (a2);
% \draw[darr] (a2) -- (drp);
\draw[darr] (a2) -- (c3);
\draw[darr] (c3) -- (bn3);
\draw[darr] (bn3) -- (add);
\draw[darr] (add) -- (outact);

% Skip path
\draw[darr] (c1.east) -| ($(proj.north)+(0,0mm)$);
\draw[darr] (proj) -- (projbn);
\draw[darr] (projbn.south) |- (add.east);

\begin{scope}[on background layer]
\node[detailbox, fit=(c1) (bn1) (a1) (c2) (bn2) (a2) (c3) (bn3) (proj) (projbn) (add) (outact)] (detail) {};
\end{scope}

\draw[dashed, line width=0.9pt] (bottleneck.north east) -- (detail.north west);
\draw[dashed, line width=0.9pt] (bottleneck.south east) -- (detail.south west);

\end{tikzpicture}

### 2025-08-24 contents/results.tex
finish results section

@@
 
-% NOT  finished
+% almost finished
 
-to write
+The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 170th among 350 submissions.
+The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.
+
+\begin{table}[!htp]
+\centering
+\begin{tabular}{r|r|r|r}
+Training & Validation & Test & Ranking \\\hline
+$0.451 \pm 0.005$ & 0.245 & TBA & 170/350 \\\hline
+\end{tabular}
+\caption{Challenge scores for our submitted entries (team ``Revenger'').
+Training: internal hold-out mean $\pm$ std over repeated runs.
+Validation: best among 10 validation submissions.
+Test: to be announced.
+Ranking: position on the hidden validation leaderboard.}
+\label{tab:scores}
+\end{table}

### 2025-08-25 contents/discussions.tex
finish the Discussion and Conclusions section

@@
 
-% NOT finished.
+% almost finished.
 
-to write
+The hidden validation Challenge score presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement.
+The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision.
+This is achieved through reliability-aware label smoothing, which incorporates both label provenance and reliability instead of treating all positive labels uniformly.
+Together with the asymmetric loss and strategic upsampling, these results indicate that explicitly modeling label reliability helps stabilize the learning process more effectively than introducing additional architectural complexity.
+Overall, our approach aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.
+
+However, the performance gap between our internal hold-out subset and the hidden validation set suggests two primary limitations.
+First, the reliability weights (smoothing factors) were pre-defined based on label provenance rather than learned from data.
+This static assignment cannot capture the inherent heterogeneity of label quality within each source.
+Second, positive upsampling was applied uniformly at the dataset level using fixed factors.
+This strategy overlooks variations in individual sample difficulty and does not adapt to the model's evolving confidence during training.
+Furthermore, we did not make use of the additional labels available in some datasets, such as arrhythmia labels, to design and implement auxiliary learning tasks that could have enhanced the performance of the main task, Chagas screening.
+
+Future research directions will primarily focus on the development of a self-adaptive supervision framework.
+This includes dynamic weighting schemes for learning instance-specific reliability scores, moving beyond static smoothing factors; and adaptive sampling strategies that respond to the model's evolving confidence during training, offering a promising alternative to fixed upsampling factors.
+Data augmentation techniques, such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE}, could be applied to further expand and diversify the positive samples, thereby enhancing the model's robustness.
+Additionally, a multi-task learning framework leveraging auxiliary arrhythmia labels could enhance feature representation and improve generalization for the primary Chagas screening task.

### 2025-08-25 contents/methods.tex
finish results section
finish the Discussion and Conclusions section

@@
 
-We used three ECG datasets for model training, with substantial differences in sample size, chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.
+We used three ECG datasets for model training, with substantial differences in sample size, Chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.
 
@@
 
+\begin{figure*}[!t]
+\centering
+\input{tikz_plots/resnet_nature_comm_bottle_neck}
+\caption{Model architecture.
+Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
+Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded (post-bottleneck) channels.
+Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
+The middle 15-length convolution uses stride 4 for temporal downsampling; 1$\times$1 convolutions reduce then expand channels, and a projection 1$\times$1 (stride 4) aligns resolution and width for the residual path.
+For clarity, dropout layers present in the implementation are omitted.
+Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
+\label{fig:model}
+\end{figure*}
+
 \subsection{Reliability-Aware Hierarchical Supervision}
@@
 
-Severe class imbalance was mitigated by upsampling positives during training: positive samples from CODE-15\% were upsampled by a factor of 3, and those from SaMi-Trop by 7.
+Severe class imbalance was mitigated by upsampling positives during training: positive samples from CODE-15\% were upsampled by a factor of 3, and those from SaMi-Trop by 12.
 No upsampling was applied to PTB-XL, which contains no positives.
+We chose these factors after reviewing hidden validation scores from multiple submissions, as shown in Table~\ref{tab:upsampling_schemes}.
+
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{ccc}
+\toprule
+\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Challenge score} \\
+\cmidrule(lr){1-2}
+CODE-15\% &  SaMi-Trop & \\
+\midrule
+- & -     & 0.239$^*$ \\
+3 & 7      & 0.212 \\
+3 & 12    & \textbf{0.245} \\
+10 & 120   & 0.210 \\
+6 & 36     & 0.221 \\
+\bottomrule
+\end{tabular}
+\caption{Representative upsampling schemes and corresponding Challenge scores on the hidden validation set. The model and training strategies used were the same. “-” indicates no upsampling.\\
+$^*$: obtained during the unofficial phase.
+}
+\label{tab:upsampling_schemes}
+\end{table}
+
 Smoothed labels and upsampling strategies for each dataset are summarized in Table~\ref{tab:augmentation}.
@@
 \midrule
-SaMi-Trop & $7$ & N/A           & $[0,\,1]$     \\
+SaMi-Trop & $12$ & N/A           & $[0,\,1]$     \\
 CODE-15\% & $3$ & $[0.7,\,0.3]$ & $[0.3,\,0.7]$ \\
@@
 A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
-Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$,yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.
+Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$, yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.
 
@@
 
-\begin{figure*}
-\centering
-\input{tikz_plots/resnet_nature_comm_bottle_neck}
-\caption{Model architecture.
-Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
-Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded (post-bottleneck) channels.
-Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
-The middle 15-length convolution uses stride 4 for temporal downsampling; 1$\times$1 convolutions reduce then expand channels, and a projection 1$\times$1 (stride 4) aligns resolution and width for the residual path.
-For clarity, dropout layers present in the implementation are omitted.
-Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
-\label{fig:model}
-\end{figure*}
-
-\subsection{Training and Implementation Setup}
+\subsection{Training and Implementation Setups}
 \label{subsec:train}

### 2025-08-26 contents/abstract.tex
minor updates

@@
 To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones.
-Model training used an asymmetric loss to further penalize false negatives and was optimized with Adam and a OneCycle learning rate schedule.
+Model training used an asymmetric loss to further penalize false negatives and was optimized with AdamW and a OneCycle learning rate scheduler.
 Model selection was based on the Challenge score from an internal hold-out subset.
 
-Results: In cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN].
-On the hidden validation set, our method received a Challenge score of [VAL-SCORE] (rank [VAL-RANK]).
+Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 179~/~364).
+In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
 

### 2025-08-26 contents/discussions.tex
minor updates

@@
 Together with the asymmetric loss and strategic upsampling, these results indicate that explicitly modeling label reliability helps stabilize the learning process more effectively than introducing additional architectural complexity.
-Overall, our approach aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.
+Overall, our approach offers a scalable and resource-efficient solution and aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.
 
@@
 This includes dynamic weighting schemes for learning instance-specific reliability scores, moving beyond static smoothing factors; and adaptive sampling strategies that respond to the model's evolving confidence during training, offering a promising alternative to fixed upsampling factors.
-Data augmentation techniques, such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE}, could be applied to further expand and diversify the positive samples, thereby enhancing the model's robustness.
+Data augmentation techniques, such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE}, could be applied to further expand and diversify the positive samples, thereby enhancing the model's robustness against overfitting and improving generalization to underrepresented patterns.
 Additionally, a multi-task learning framework leveraging auxiliary arrhythmia labels could enhance feature representation and improve generalization for the primary Chagas screening task.
+Exploring self-supervised pre-training on large-scale unlabeled ECG data also represents a promising direction to learn more transferable representations before fine-tuning on the target task.

### 2025-08-26 contents/methods.tex
minor updates

@@
 
+\setlength{\tabcolsep}{4pt} % Default value: 6pt
 \begin{table}[!htp]
@@
 \midrule
-SaMi-Trop & 1\,631   & 100 & expert-confirmed \\
-CODE-15\% & 345\,779 & 1.795   & self-reported \\
-PTB-XL    & 21\,799  & 0   & N/A \\
+SaMi-Trop   & 1\,631     & 100 \%    & expert-confirmed \\
+CODE-15\%   & 345\,779   & 1.795 \%  & self-reported \\
+PTB-XL      & 21\,799    & 0 \%      & N/A \\
 \bottomrule
@@
 \end{table}
+\setlength{\tabcolsep}{6pt} % Default value: 6pt
 
@@
 where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_x$ and $\boldsymbol{\sigma}_x$ are the mean and standard deviation of $\mathbf{x}$, respectively.
-We excluded ECGs shorter than 1,200 samples to ensure inputs contain enough cardiac cycles for stable model analysis.
+We excluded ECGs shorter than 1200 samples to ensure inputs contain enough cardiac cycles for stable model analysis.
 
@@
 Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
-Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded (post-bottleneck) channels.
+Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
 Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
-The middle 15-length convolution uses stride 4 for temporal downsampling; 1$\times$1 convolutions reduce then expand channels, and a projection 1$\times$1 (stride 4) aligns resolution and width for the residual path.
+The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path.
 For clarity, dropout layers present in the implementation are omitted.
@@
 \caption{Representative upsampling schemes and corresponding Challenge scores on the hidden validation set. The model and training strategies used were the same. “-” indicates no upsampling.\\
-$^*$: obtained during the unofficial phase.
+$^*$ obtained during the unofficial phase.
 }
@@
 
-\textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of the form $1$–$15$–$1$ (pointwise--temporal--pointwise).
-The middle temporal convolution (kernel size 15) applies stride 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4.
+\textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of kernel sizes $1$–$15$–$1$ (pointwise--temporal--pointwise).
+The middle temporal convolution applies a stride of 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4.
 A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
@@
 where $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $\delta=0.05$.
-We train for 30 epochs with batch size 128 using AdamW (AMSGrad, initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle schedule, weight decay $1\times10^{-2}$).
+We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle scheduler, weight decay $1\times10^{-2}$).
 Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric.
 Each training segment is a uniform random crop (or center trim if shorter) of length 4,096 samples.
-All components (data pipeline, optimization utilities) are implemented using the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.
+The full implementation, including model construction, data pipeline, and optimization utilities, is based on the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.

### 2025-08-26 tikz_plots/resnet_nature_comm_bottle_neck.tex
finish results section
minor updates

@@
     every node/.style={inner sep=2pt},
-    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
+    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                  align=center, fill=blue!10},
@@
                   align=center, fill=orange!12},
-    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
+    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                align=center, fill=green!12},
-    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
+    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                  align=center, fill=cyan!10},
-    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=10mm,
+    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                  align=center, fill=purple!10},
-    output/.style={draw, rounded corners=2pt, minimum width=24mm, minimum height=10mm,
+    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=red!10},
@@
     ann/.style={inner sep=1pt, align=center},
-    layer/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
+    layer/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                   align=center, fill=blue!6},
-    bnact/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
+    bnact/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                   align=center, fill=violet!10},
-    act/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
+    act/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                   align=center, fill=red!10},
-    drop/.style={draw, rounded corners=2pt, minimum width=18mm, minimum height=6.2mm,
+    drop/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                   align=center, fill=gray!15, dashed},
@@
 % Compressed single bottleneck block (represents 4 stacked blocks)
-\node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1 (stride=4) \\ Ch: $512 \to 768 \to 1024 \to 1280$};
+% \node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1 \\ Ch: $512 \to 768 \to 1024 \to 1280$};
+
+\node[block, below=of stem, minimum height=0pt] (bottleneck) {%
+\begin{tikzpicture}[baseline=(ch.base), node distance=1mm]
+\node[inner sep=2pt] (core)
+{Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1};
+\draw[rounded corners=1pt] (core.north west) rectangle (core.south east);
+\node[minimum width=2mm, left=of core] {\larger[3] $\mathbf{4\times}$};
+\node[below left=1mm and -20mm of core.south, inner sep=2pt] (ch) {Ch: $512 \to 768 \to 1024 \to 1280$};
+\end{tikzpicture}
+};
 
@@
 
-\node[layer, below=0mm of expandAnchor] (c1) {Conv 1$\times$1};
+\node[layer, below=-0.5mm of expandAnchor] (c1) {Conv ks=1};
 \node[below right=-1mm and 8mm of c1.south] {reduce};
@@
 
-\node[layer, below=5mm of a1] (c2) {Conv 15\\(stride 4)};
+\node[layer, below=5mm of a1] (c2) {Conv ks=15\\(stride 4)};
 \node[bnact, below=5mm of c2] (bn2) {BN};
@@
 
-\node[layer, below=5mm of a2] (c3) {Conv 1$\times$1};
+\node[layer, below=5mm of a2] (c3) {Conv ks=1};
 \node[below right=-1mm and 8mm of c3.south] {expand};
@@
 \node[sum, below=5mm of bn3] (add) {+};
-\node[act, below=5mm of add] (outact) {ReLU (output)};
+\node[act, below=5mm of add] (outact) {ReLU};
 
 % Projection/skip branch (since stride=4 or channel change)
-\node[layer, right=10mm of c2, yshift=-7mm, minimum width=18mm] (proj) {Proj 1$\times$1 \\ (stride 4)};
-\node[bnact, below=5mm of proj, minimum width=18mm] (projbn) {BN};
+\node[layer, right=10mm of c2, yshift=-7mm, minimum width=19mm] (proj) {Proj Conv \\ (stride 4)};
+\node[bnact, below=5mm of proj, minimum width=19mm] (projbn) {BN};
 

### 2025-08-28 paper_short_in_one.tex
add aggregated file paper_short_in_one.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compiler: pdfLaTeX
% TeX Live version: 2024
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \ifdefined\ifhandout\else
\newif\ifhandout
% \fi

% NOTE: for the final version, set \handouttrue
% \handoutfalse
\handouttrue

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% unofficial phase abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \input{contents/unofficial_abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% conference short paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% preamble

\documentclass[twocolumn]{cinc}

\usepackage[T1]{fontenc}
\usepackage{mathtools, graphicx, xurl, hyperref}
% \usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows.meta, decorations.pathmorphing, decorations.pathreplacing, backgrounds, positioning, fit, calc, shadows, shapes.misc}
% \tikzexternalize[prefix=tikz/,optimize command away=\includepdf]
\usepackage{boldline, multirow}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{colortbl}
\usepackage{subcaption}
\usepackage{relsize}
\usepackage{fontawesome5}
\usepackage[ruled, vlined]{algorithm2e}

\usepackage{tabularx} % for 'X' col. type and 'tabularx' environment
\usepackage{ragged2e} % for '\RaggedRight' macro
\newcolumntype{L}{>{\RaggedRight}X} % disable full justification

% \tikzstyle{smallcircleblock} = [circle, draw, text width = 0.7em, text centered]

% \tikzstyle{wideblock} = [rectangle, draw, text width = 6.5em, text centered, rounded corners, inner sep = 7pt, minimum height = 1.0em]

\newcommand\ImageNode[4][]{
  \node[#1] (#2) {\includegraphics[#3]{#4}};
}
\definecolor{arrowblue}{RGB}{98,145,224}

\newcolumntype{g}{>{\columncolor[gray]{0.8}}l}

\newif\ifcoloredtext
\coloredtextfalse

\newif\ifboxednn
\boxednntrue

\newenvironment{indentedquote}[1]%
{\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
{\endlist}

\newcommand\wordcount{\input{|"texcount -inc -sum -0 -utf8 -ch -template={SUM} \currfilepath"}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% title, author, institution

\title{Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity}
\author{Hao Wen\textsuperscript{1},
Jingsu Kang\textsuperscript{2} \\ \ \\
\textsuperscript{1}College of Science, China Agricultural University, Beijing, China\\
\textsuperscript{2}Tianjin Medical University, Tianjin, China
}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% abstract
\begin{abstract}

% almost finished

% --------------------------------------------------
% Unofficial phase version:

% Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B. Moody PhysioNet Challenge 2025.

% Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance. We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive). The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported. We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones. Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability). Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence. A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.

% Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.

% Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
% --------------------------------------------------

Aim: We present a reliability-aware hierarchical learning framework for ECG-based Chagas cardiomyopathy screening in the George B. Moody PhysioNet Challenge 2025 by Team Revenger, aiming to maximize positive case retrieval under prevalence constraints.

Methods: The 12-lead ECGs were resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized. We used a ResNet model integrated with squeeze-and-excitation (SE) modules for binary classification. To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones. Model training used an asymmetric loss to further penalize false negatives and was optimized with AdamW and a OneCycle learning rate scheduler. Model selection was based on the Challenge score from an internal hold-out subset.

Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 179~/~364). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.

Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.

\end{abstract}

% main body of the paper

\section{Introduction}
\label{sec:intro}

% almost finished

Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B. Moody PhysioNet Challenge \cite{goldberger2000physionet, cinc2025}. Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.

In this work, we propose a reliability-aware hierarchical framework that prioritizes expert-confirmed labels and mitigates severe class imbalance within a deep ECG model, with optimization aligned to prevalence-constrained sensitivity objectives.

\section{Methods}
\label{sec:methods}

% almost finished

\subsection{Datasets and Preprocessing}
\label{subsec:data}

% almost finished

We used three ECG datasets for model training, with substantial differences in sample size, Chagas prevalence, and label provenance as summarized in Table~\ref{tab:dataset_stats}.

\setlength{\tabcolsep}{4pt} % Default value: 6pt
\begin{table}[!htp]
\centering
\begin{tabular}{rlll}
\toprule
Dataset & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Chagas rate} & Label provenance \\
\midrule
SaMi-Trop   & 1\,631     & 100 \%    & expert-confirmed \\
CODE-15\%   & 345\,779   & 1.795 \%  & self-reported \\
PTB-XL      & 21\,799    & 0 \%      & N/A \\
\bottomrule
\end{tabular}
\caption{Dataset statistics and label provenance. Chagas rate is the proportion of recordings labeled positive in each dataset. N/A indicates that confirmed Chagas cases are not expected (non-endemic population).}
\label{tab:dataset_stats}
\end{table}
\setlength{\tabcolsep}{6pt} % Default value: 6pt

All ECGs were uniformly resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized to zero mean and unit variance computed as in Eq.~\ref{eq:z_score}:
\begin{equation}
\label{eq:z_score}
\tilde{\mathbf{x}} = \frac{\mathbf{x} - \boldsymbol{\mu}_x}{\boldsymbol{\sigma}_x}
\end{equation}
where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_x$ and $\boldsymbol{\sigma}_x$ are the mean and standard deviation of $\mathbf{x}$, respectively. We excluded ECGs shorter than 1200 samples to ensure inputs contain enough cardiac cycles for stable model analysis.

\begin{figure*}[!t]
\centering
\begin{tikzpicture}[
    % font=\small,
    line width=0.75pt,
    >={Latex[length=3mm]},
    node distance=6.4mm,
    every node/.style={inner sep=2pt},
    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=blue!10},
    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
                  align=center, fill=orange!12},
    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
               align=center, fill=green!12},
    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=cyan!10},
    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=purple!10},
    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                align=center, fill=red!10},
    arrow/.style={-{Latex[length=3mm]}, thick},
    darr/.style={-{Latex[length=2.4mm]}, thick},
    dashedarrow/.style={-{Latex[length=2.6mm]}, thick, dashed},
    ann/.style={inner sep=1pt, align=center},
    layer/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=blue!6},
    bnact/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=violet!10},
    act/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=red!10},
    drop/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=gray!15, dashed},
    sum/.style={draw, circle, inner sep=1.6pt, fill=white},
    % brace/.style={decorate, decoration={brace, amplitude=6pt}},
    detailbox/.style={draw, rounded corners=3pt, inner sep=6pt, fill=orange!3}
]

% ================= Left (overall vertical path) =================
\node[stem] (input) {Input \\ (12$\times$L)};
\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};

% Compressed single bottleneck block (represents 4 stacked blocks)
% \node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1 \\ Ch: $512 \to 768 \to 1024 \to 1280$};

\node[block, below=of stem, minimum height=0pt] (bottleneck) {%
\begin{tikzpicture}[baseline=(ch.base), node distance=1mm]
\node[inner sep=2pt] (core)
{Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1};
\draw[rounded corners=1pt] (core.north west) rectangle (core.south east);
\node[minimum width=2mm, left=of core] {\larger[3] $\mathbf{4\times}$};
\node[below left=1mm and -20mm of core.south, inner sep=2pt] (ch) {Ch: $512 \to 768 \to 1024 \to 1280$};
\end{tikzpicture}
};

% Global SE
\node[se, below=of bottleneck] (gse) {Global SE \\ reduction=8};

% Global pooling
\node[pool, below=of gse] (gap) {Global MaxPool};

% MLP Head
\node[head, below=of gap] (mlp) {MLP Head \\ (1280 $\rightarrow$ C=2)};

% Output
\node[output, below=of mlp] (out) {Output Logits};

% Arrows (overall path)
\draw[arrow] (input) -- (stem);
\draw[arrow] (stem) -- (bottleneck);
\draw[arrow] (bottleneck) -- (gse);
\draw[arrow] (gse) -- (gap);
\draw[arrow] (gap) -- (mlp);
\draw[arrow] (mlp) -- (out);

% ================= Right (expanded single bottleneck internals) =================
% Anchor for expansion (to the right of overall bottleneck block)
\coordinate (expandAnchor) at ($(input.east)+(45mm,0)$);

\node[layer, below=-0.5mm of expandAnchor] (c1) {Conv ks=1};
\node[below right=-1mm and 8mm of c1.south] {reduce};
\node[bnact, below=5mm of c1] (bn1) {BN};
\node[act, below=5mm of bn1] (a1) {ReLU};

\node[layer, below=5mm of a1] (c2) {Conv ks=15\\(stride 4)};
\node[bnact, below=5mm of c2] (bn2) {BN};
\node[act, below=5mm of bn2] (a2) {ReLU};
% \node[drop, below=5mm of a2] (drp) {Dropout 0.2};

\node[layer, below=5mm of a2] (c3) {Conv ks=1};
\node[below right=-1mm and 8mm of c3.south] {expand};
\node[bnact, below=5mm of c3] (bn3) {BN};

\node[sum, below=5mm of bn3] (add) {+};
\node[act, below=5mm of add] (outact) {ReLU};

% Projection/skip branch (since stride=4 or channel change)
\node[layer, right=10mm of c2, yshift=-7mm, minimum width=19mm] (proj) {Proj Conv \\ (stride 4)};
\node[bnact, below=5mm of proj, minimum width=19mm] (projbn) {BN};

% Connections internal
\draw[darr] (c1) -- (bn1);
\draw[darr] (bn1) -- (a1);
\draw[darr] (a1) -- (c2);
\draw[darr] (c2) -- (bn2);
\draw[darr] (bn2) -- (a2);
% \draw[darr] (a2) -- (drp);
\draw[darr] (a2) -- (c3);
\draw[darr] (c3) -- (bn3);
\draw[darr] (bn3) -- (add);
\draw[darr] (add) -- (outact);

% Skip path
\draw[darr] (c1.east) -| ($(proj.north)+(0,0mm)$);
\draw[darr] (proj) -- (projbn);
\draw[darr] (projbn.south) |- (add.east);

\begin{scope}[on background layer]
\node[detailbox, fit=(c1) (bn1) (a1) (c2) (bn2) (a2) (c3) (bn3) (proj) (projbn) (add) (outact)] (detail) {};
\end{scope}

\draw[dashed, line width=0.9pt] (bottleneck.north east) -- (detail.north west);
\draw[dashed, line width=0.9pt] (bottleneck.south east) -- (detail.south west);

\end{tikzpicture}

\caption{Model architecture. Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits. Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise). The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path. For clarity, dropout layers present in the implementation are omitted. Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
\label{fig:model}
\end{figure*}

\subsection{Reliability-Aware Hierarchical Supervision}
\label{subsec:reliability}

% almost finished

We introduce a hierarchical supervision scheme that encodes source reliability through stratified label smoothing and adaptive upsampling. Three reliability levels are defined: (1) expert-confirmed positives (SaMi-Trop, maximal trust), (2) self-reported samples (CODE-15\%, both positives and negatives, higher uncertainty), and (3) non-endemic negatives (PTB-XL, very low true prevalence but still mildly regularized). Given a one-hot label $\mathbf{y}$ ($[0, 1]$ for positives, $[1, 0]$ for negatives) and number of classes $C = 2,$ the smoothed target is computed as in Eq.~\ref{eq:label_smoothing}:
\begin{equation}
\label{eq:label_smoothing}
\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1},
\end{equation}
where $\varepsilon$ is the smoothing factor which depends on the reliability level: 0.0 (SaMi positives), 0.6 (CODE-15\% positives \& negatives), 0.2 (PTB-XL negatives). This attenuates overconfident gradients for noisier or potentially misreported labels while preserving sharp supervision on expert-confirmed cases.

Severe class imbalance was mitigated by upsampling positives during training: positive samples from CODE-15\% were upsampled by a factor of 3, and those from SaMi-Trop by 12. No upsampling was applied to PTB-XL, which contains no positives. We chose these factors after reviewing hidden validation scores from multiple submissions, as shown in Table~\ref{tab:upsampling_schemes}.

\begin{table}[!htbp]
\centering
\begin{tabular}{ccc}
\toprule
\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Challenge score} \\
\cmidrule(lr){1-2}
CODE-15\% &  SaMi-Trop & \\
\midrule
- & -     & 0.239$^*$ \\
3 & 7      & 0.212 \\
3 & 12    & \textbf{0.245} \\
10 & 120   & 0.210 \\
6 & 36     & 0.221 \\
\bottomrule
\end{tabular}
\caption{Representative upsampling schemes and corresponding Challenge scores on the hidden validation set. The model and training strategies used were the same. “-” indicates no upsampling.\\
$^*$ obtained during the unofficial phase.
}
\label{tab:upsampling_schemes}
\end{table}

Smoothed labels and upsampling strategies for each dataset are summarized in Table~\ref{tab:augmentation}.

\begin{table}[!htp]
\centering
\begin{tabular}{lcccc}
\toprule
\multirow{2}{*}{Dataset} & Upsampling & \multicolumn{2}{c}{Smoothed labels} \\ \cmidrule(lr){3-4}
& factor & negative & positive \\
\midrule
SaMi-Trop & $12$ & N/A           & $[0,\,1]$     \\
CODE-15\% & $3$ & $[0.7,\,0.3]$ & $[0.3,\,0.7]$ \\
PTB-XL    & $1$ & $[0.9,\,0.1]$ & N/A           \\
\bottomrule
\end{tabular}
\caption{Smoothed labels (computed from Eq.~\ref{eq:label_smoothing}) and upsampling strategies for each dataset.}
\label{tab:augmentation}
\end{table}

\subsection{Model Architecture}
\label{subsec:model}

% almost finished

We build upon the 1D ResNet ECG classifier of Ribeiro et al.~\cite{ribeiro2020automatic} and introduce three modifications.

\textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of kernel sizes $1$–$15$–$1$ (pointwise--temporal--pointwise). The middle temporal convolution applies a stride of 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4. A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes. Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$, yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.

\textbf{(2) Global squeeze-and-excitation (SE).} After the final bottleneck block, a single global SE module (reduction ratio 8) \cite{hu2018senet} performs temporal average pooling to a channel descriptor, applies a two-layer bottleneck multi-layer perceptron (MLP) $1280 \to 160 \to 1280$ with ReLU and sigmoid gating, and rescales the feature map channel-wise.

\textbf{(3) Global pooling head for variable input length.} Instead of flattening a fixed-length feature map as in the original baseline, we apply global max pooling over the remaining temporal dimension, yielding a 1280-dimensional vector irrespective of input length $L$. This vector is fed to a lightweight two-layer classification MLP: a hidden fully connected layer ($1280 \to 1024$) with non-linear activation and dropout (rate 0.2), followed by a final linear layer ($1024 \to 2$) producing class logits.

\textbf{Stem and regularization.} A stem Conv1d (kernel size 15, stride 1, 64 channels) with BatchNorm and ReLU precedes the bottleneck stack. Within each bottleneck block we apply BatchNorm+ReLU after the first two convolutions and dropout (rate 0.2) after each of those activations. All convolutions use “same” padding to preserve temporal length before downsampling operations.

Overall, the changes primarily enable variable-length inference and add global channel reweighting with minimal structural overhead. The resulting model architecture is illustrated in Fig.~\ref{fig:model}.

\subsection{Training and Implementation Setups}
\label{subsec:train}

% almost finished

We employed an asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to further complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance. Let $z$ denote the logits and $p=\sigma(z)$ the predicted probability of the Chagas-positive class, the ASL is defined in Eq.~\ref{eq:asl} with separate focusing parameters for positives and negatives and a clipped negative probability:
\begin{equation}
\label{eq:asl}
\begin{multlined}
L = -y \cdot (1-p)^{\gamma_{+}} \log(p) \\
\phantom{L = } - (1-y) \cdot (p_m)^{\gamma_{-}} \log(1-p_m),
\end{multlined}
\end{equation}
where $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $\delta=0.05$. We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle scheduler, weight decay $1\times10^{-2}$). Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric. Each training segment is a uniform random crop (or center trim if shorter) of length 4,096 samples. The full implementation, including model construction, data pipeline, and optimization utilities, is based on the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.

\section{Results}
\label{sec:results}

% almost finished

The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 170th among 350 submissions. The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.

\begin{table}[!htp]
\centering
\begin{tabular}{r|r|r|r}
Training & Validation & Test & Ranking \\\hline
$0.451 \pm 0.005$ & 0.245 & TBA & 179~/~364 \\\hline
\end{tabular}
\caption{Challenge scores for our submitted entries (team ``Revenger''). Training: internal hold-out mean $\pm$ std over repeated runs. Validation: best among 10 validation submissions. Test: to be announced. Ranking: position on the hidden validation leaderboard.}
\label{tab:scores}
\end{table}

\section{Discussion and Conclusions}
\label{sec:discu}

% almost finished.

The hidden validation Challenge score presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement. The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision. This is achieved through reliability-aware label smoothing, which incorporates both label provenance and reliability instead of treating all positive labels uniformly. Together with the asymmetric loss and strategic upsampling, these results indicate that explicitly modeling label reliability helps stabilize the learning process more effectively than introducing additional architectural complexity. Overall, our approach offers a scalable and resource-efficient solution and aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.

However, the performance gap between our internal hold-out subset and the hidden validation set suggests two primary limitations. First, the reliability weights (smoothing factors) were pre-defined based on label provenance rather than learned from data. This static assignment cannot capture the inherent heterogeneity of label quality within each source. Second, positive upsampling was applied uniformly at the dataset level using fixed factors. This strategy overlooks variations in individual sample difficulty and does not adapt to the model's evolving confidence during training. Furthermore, we did not make use of the additional labels available in some datasets, such as arrhythmia labels, to design and implement auxiliary learning tasks that could have enhanced the performance of the main task, Chagas screening.

Future research directions will primarily focus on the development of a self-adaptive supervision framework. This includes dynamic weighting schemes for learning instance-specific reliability scores, moving beyond static smoothing factors; and adaptive sampling strategies that respond to the model's evolving confidence during training, offering a promising alternative to fixed upsampling factors. Data augmentation techniques, such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE}, could be applied to further expand and diversify the positive samples, thereby enhancing the model's robustness against overfitting and improving generalization to underrepresented patterns. Additionally, a multi-task learning framework leveraging auxiliary arrhythmia labels could enhance feature representation and improve generalization for the primary Chagas screening task. Exploring self-supervised pre-training on large-scale unlabeled ECG data also represents a promising direction to learn more transferable representations before fine-tuning on the target task.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% acknowledgments

% \input{contents/acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{cinc}
\bibliography{references}
% \bibliography{references-reduced}

\begin{correspondence}
Hao Wen\\
No. 17, Qinghua East Road, Haidian District, Beijing, China\\
wenh06@cau.edu.cn,wenh06@gmail.com
\end{correspondence}

\balance

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% conference poster
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \input{poster}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% long paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \input{paper_long}

### 2025-08-28 poster.tex
Complete poster.tex for 2025 Chagas ECG screening challenge
Co-authored-by: wenh06 <8778305+wenh06@users.noreply.github.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% NIWeek 2014 Poster by T. Reveyrand
-% www.microwave.fr
-% http://www.microwave.fr/LaTeX.html
-% ---------------------------------------
+% 2025 PhysioNet/CinC Challenge Poster
+% Chagas ECG Screening - Team Revenger
 % 
-% Original template created by:
-% Brian Amberg (baposter@brian-amberg.de)
-%
-% This template has been downloaded from:
-% http://www.LaTeXTemplates.com
-%
-% License:
-% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
-%
+% Based on baposter template by T. Reveyrand
+% Original template by Brian Amberg (baposter@brian-amberg.de)
+% Downloaded from: http://www.LaTeXTemplates.com
+% License: CC BY-NC-SA 3.0
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{textcomp}
-
 \usepackage{hyperref}
@@
 
+% Color definitions (reusing 2024 poster color scheme)
 \definecolor{bordercol}{RGB}{40,40,40} % Border color of content boxes
@@
 \definecolor{jdhblue}{RGB}{2,93,186}
-
 \definecolor{zkblue}{RGB}{88,135,175}
@@
 
-% \usetikzlibrary{shapes, arrows, external, decorations.pathmorphing, backgrounds, positioning, fit, petri, calc, hobby, cd}
-
 \begin{document}
-
-% \background{ % Set the background to an image (background.pdf)
-% \begin{tikzpicture}[remember picture,overlay]
-% \draw (current page.north west)+(-2em,2em) node[anchor=north west]
-% {\includegraphics[height=1.1\textheight]{images/baposter_background.pdf}};
-% \end{tikzpicture}
-% }
 
@@
 headerFontColor=headerfontcol, % Text color for the header text in the content boxes
-% boxColorOne=boxcolor, % Background color for the content in the content boxes
 boxColorOne=zkbackground,
@@
 textborder=rectangle,
-% background=user,
 background=none,
@@
 %
-{\includegraphics[scale=0.401]{images/logo_cau_science.png}} % University/lab logo
+% TODO: Add logos when available - current paths may not exist
+% \IfFileExists{images/logo_cau_science.png}{\includegraphics[scale=0.401]{images/logo_cau_science.png}}{CAU Logo}
+{{\bf TODO: CAU Logo}} % University/lab logo placeholder
 {
-{\bf \fontsize{19pt}{19pt} \selectfont To write}
+{\bf \fontsize{18pt}{18pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity}
 } % Poster title
@@
 
-$^1${\it College of Science, China Agricultural University}\qquad
+$^1${\it College of Science, China Agricultural University}\\
 $^2${\it Tianjin Medical University} \\
 \vspace{0.2cm}
-{\Large \bf{The George B. Moody PhysioNet Challenge 2025}, ~~~\bf{Team Revenger}}
+{\Large \bf{The George B. Moody PhysioNet Challenge 2025} $\cdot$ \bf{Team Revenger}}
 }
-{\includegraphics[scale=0.101]{logo_tmu.jpeg}}
-
-\newif\ifcoloredtext
-\coloredtexttrue
-\newif\ifboxednn
-\boxednntrue
+% \IfFileExists{logo_tmu.jpeg}{\includegraphics[scale=0.101]{logo_tmu.jpeg}}{TMU Logo}
+{{\bf TODO: TMU Logo}} % University logo placeholder
 
 %----------------------------------------------------------------------------------------
-%	INTRODUCTION
+%	INTRODUCTION & CHALLENGE CONTEXT
 %----------------------------------------------------------------------------------------
 
-\headerbox{Introduction}{name=introduction, column=0, row=0, span=3}{
-% finished
+\headerbox{Introduction \& Challenge Context}{name=introduction, column=0, row=0, span=3}{
 
 \begin{itemize}
-\item to write
-\vspace{-0.2cm}
-\item to write
-\vspace{-0.2cm}
-\item to write
+\item {\bf Team Revenger – PhysioNet Challenge 2025}: ECG-based Chagas cardiomyopathy screening in resource-limited settings
+\item {\bf Challenge objective}: Maximize positive case retrieval under 5\% prevalence constraint for scalable screening
+\item {\bf Key challenge}: Severe class imbalance ($\sim$2\% positives) + expert label scarcity (0.2\% expert-confirmed)
+\item {\bf Our approach}: Reliability-aware hierarchical learning prioritizing expert-confirmed over self-reported labels
 \end{itemize}
+
 }
@@
 %----------------------------------------------------------------------------------------
-%	Framework
+%	DATA & LABEL PROVENANCE
 %----------------------------------------------------------------------------------------
 
-\headerbox{The Multi-Stage Framework}{name=framework, column=0, span=3, row=1, below=introduction}{
-% finished
+\headerbox{Data \& Label Provenance}{name=data, column=0, row=1, span=2, below=introduction}{
 
-\newif\ifFrameworkFigBox
-\FrameworkFigBoxfalse
+Three ECG datasets with heterogeneous label reliability and Chagas prevalence:
 
+\vspace{0.3cm}
 \begin{center}
-\input{tikz_plots/multi-stage-framework}
+\begin{tabular}{rlll}
+\toprule
+Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source \\
+\midrule
+SaMi-Trop   & 1,631     & 100.0 \%    & expert-confirmed \\
+CODE-15\%   & 345,779   & 1.8 \%      & self-reported \\
+PTB-XL      & 21,799    & 0.0 \%      & N/A (non-endemic) \\
+\bottomrule
+\end{tabular}
+\end{center}
+\vspace{0.3cm}
+
+\begin{itemize}
+\item {\bf Preprocessing}: Resampled to 400 Hz, bandpass filtered (0.5–45 Hz), z-score normalized
+\item {\bf Challenge}: Model must learn from heterogeneous label quality and extreme class imbalance
+\end{itemize}
+
+}
+
+%----------------------------------------------------------------------------------------
+%	RELIABILITY-AWARE SUPERVISION
+%----------------------------------------------------------------------------------------
+
+\headerbox{Reliability-Aware Supervision}{name=supervision, column=2, row=1, span=1, below=introduction}{
+
+{\bf Label Smoothing \& Upsampling Strategy}
+
+Hierarchical supervision encoding source reliability through stratified label smoothing:
+
+\vspace{0.2cm}
+{\bf Formula:} $\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}$
+\vspace{0.2cm}
+
+Where smoothing factor $\varepsilon$ depends on reliability:
+\begin{itemize}
+\item SaMi positives: $\varepsilon = 0.0$ (max trust)
+\item CODE-15\% samples: $\varepsilon = 0.6$ (uncertainty)  
+\item PTB-XL negatives: $\varepsilon = 0.2$ (mild regularization)
+\end{itemize}
+
+\vspace{0.3cm}
+\begin{center}
+\begin{tabular}{ccc}
+\toprule
+\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Score} \\
+\cmidrule(lr){1-2}
+CODE & SaMi & \\
+\midrule
+3 & 12    & \textbf{0.245} \\
+3 & 7     & 0.212 \\
+10 & 120   & 0.210 \\
+\bottomrule
+\end{tabular}
 \end{center}
@@
 %----------------------------------------------------------------------------------------
-%	Preprocessing
+%	MODEL ARCHITECTURE
 %----------------------------------------------------------------------------------------
 
-\headerbox{Training Data Preparation}{name=data, column=0, row=1, span=2, below=framework}{
-% finished
+\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=2, below=data}{
+
+{\bf Enhanced 1D ResNet with SE Modules \& Global Pooling}
+
+\begin{center}
+\resizebox{0.95\linewidth}{!}{%
+\begin{tikzpicture}[
+    line width=0.75pt,
+    >={Latex[length=3mm]},
+    node distance=6.4mm,
+    every node/.style={inner sep=2pt},
+    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
+                 align=center, fill=blue!10},
+    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
+                  align=center, fill=orange!12},
+    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
+               align=center, fill=green!12},
+    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
+                 align=center, fill=cyan!10},
+    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
+                 align=center, fill=purple!10},
+    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
+                align=center, fill=red!10},
+    arrow/.style={-{Latex[length=3mm]}, thick},
+]
+
+% Main architecture path
+\node[stem] (input) {Input \\ (12$\times$L)};
+\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};
+\node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1 \\ Ch: $512 \to 768 \to 1024 \to 1280$};
+\node[se, below=of bottleneck] (gse) {Global SE \\ reduction=8};
+\node[pool, below=of gse] (gap) {Global MaxPool};
+\node[head, below=of gap] (mlp) {MLP Head \\ (1280 $\rightarrow$ C=2)};
+\node[output, below=of mlp] (out) {Output Logits};
+
+% Arrows
+\draw[arrow] (input) -- (stem);
+\draw[arrow] (stem) -- (bottleneck);
+\draw[arrow] (bottleneck) -- (gse);
+\draw[arrow] (gse) -- (gap);
+\draw[arrow] (gap) -- (mlp);
+\draw[arrow] (mlp) -- (out);
+
+\end{tikzpicture}
+}
+\end{center}
 
 \begin{itemize}
-\item ECG-Image-Kit to generate ECG images from the PTB-XL dataset for our method development. Additionally, the PTB-XL+ dataset was used to generate classification labels.
-\vspace{-0.2cm}
-\item Image generation setup included augmentations such as random Gaussian noise, random color temperature adjustments, and distortions including handwritten notes, wrinkles, and creases.
-\vspace{-0.2cm}
-\item Bounding boxes for the printed waveforms and lead names, along with the plotted pixel coordinates of the waveforms, were recorded in metadata files alongside the generated images to train object detection models and segmentation models respectively.
+\item {\bf Bottleneck blocks}: 1$\times$1–15$\times$1 convolutions with expansion factor 4, stride 4 downsampling
+\item {\bf Global SE}: Channel attention with reduction ratio 8 for temporal feature recalibration  
+\item {\bf Variable-length inputs}: Global max pooling enables inference on ECGs of any duration
 \end{itemize}
@@
 %----------------------------------------------------------------------------------------
-%	Model selection
+%	TRAINING & OPTIMIZATION
 %----------------------------------------------------------------------------------------
 
-\headerbox{Model Selection}{name=nn, column=2, span=1, row = 2, below=framework}{
-% NOT finished
+\headerbox{Training \& Optimization}{name=training, column=2, row=2, span=1, below=supervision}{
 
-\input{tables/model_select_poster}
+{\bf Asymmetric Loss \& Optimization Setup}
 
-Models are chosen based on performance, efficiency, and compatibility with ECG image data.
-\newline
-\faHandPointRight[regular] DETR: 0.9 mAP \hfill \faHandPointRight[regular] U-Net: 0.73 Dice.
-\newline
-\faHandPointRight[regular] Total inference time: 2s on single RTX 3090
+\begin{itemize}
+\item {\bf Asymmetric Loss}: $L = -y(1-p)^{\gamma_{+}} \log(p) - (1-y)(p_m)^{\gamma_{-}} \log(1-p_m)$
+\item Parameters: $(\gamma_{+},\gamma_{-})=(1,4)$, margin $\delta=0.05$
+\item {\bf Optimizer}: AdamW with OneCycle scheduler
+\item {\bf Learning rate}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
+\item {\bf Training}: 30 epochs, batch size 128, weight decay $1 \times 10^{-2}$
+\item {\bf Input}: 4,096 samples (uniform crop/center trim)
+\item {\bf Early stopping}: Challenge score on 20\% internal hold-out
+\end{itemize}
 
@@
 %----------------------------------------------------------------------------------------
-%	Novel loss functions
+%	RESULTS
 %----------------------------------------------------------------------------------------
 
-\headerbox{Loss Functions}{name=loss, span=2, column=0, below=data}{
-% finished
+\headerbox{Results}{name=results, column=0, row=3, span=3, below=architecture}{
 
-\begin{tikzpicture}
-\ImageNode[]{wtmask}{width=0.4\linewidth}{images/weight-mask.pdf}
-\node [rectangle, text width = 8.8cm, inner sep = 2pt, minimum height = 1.0em, right=0.3cm of wtmask.north east, anchor=north west] {\faHandPointRight[regular] Segmentation: Since ECG waveforms occupy only a small portion of the image, we used the BCE loss multiplied by a \textbf{\color{red} weight mask} to balance the loss contribution from different parts of the ECG waveforms.
-The weight mask is the sum of multiple dilations (e.g., dilation iterations 2, 4, 6, and 8) of the binarized ground truth mask.
-On the left is an example of a weight mask.};
-\end{tikzpicture}
-\faHandPointRight[regular] Classification: Asymmetric loss $L = -y \cdot (1-p)^{\gamma_{+}} \log(p) - (1-y) \cdot (p_m)^{\gamma_{-}} \log(1-p_m)$
-\newline
-\faHandPointRight[regular] Object detection: 1 $\times$ bbox class cross-entropy + 5 $\times$ bbox coordinate L1 loss + 2 $\times$ GIoU loss
+{\bf Challenge Performance \& Analysis}
+
+\begin{center}
+\begin{tabular}{r|r|r|r}
+Internal hold-out (mean±std) & Hidden validation & Rank & Test \\
+\hline
+$0.451 \pm 0.005$ & 0.245 & 179/364 & TBA \\
+\hline
+\end{tabular}
+\end{center}
+
+\begin{itemize}
+\item {\bf Hidden validation score}: 0.245 (Challenge metric: TPR at 5\% prevalence constraint)
+\item {\bf Performance gap}: Internal vs. hidden suggests domain shift or overfitting to public data
+\item {\bf Key insight}: Reliability-aware supervision stabilizes learning under noisy labels more effectively than architectural complexity alone
+\end{itemize}
 
@@
 %----------------------------------------------------------------------------------------
-%	Submission Results
+%	DISCUSSION & INSIGHTS
 %----------------------------------------------------------------------------------------
 
-\headerbox{Submission Results}{name=submission, span=1, column=2, below=nn}{
-% NOT finished
+\headerbox{Discussion \& Insights}{name=discussion, column=0, row=4, span=2, below=results}{
 
-\begin{center}
-\input{tables/final_results_simple}
-\end{center}
-The rankings are based on the hidden validation set. Results on the public training data (more specifically, the left-out validation set) are also provided for reference.
+{\bf How does the approach provide insight into the Challenge issues?}
+
+\begin{itemize}
+\item {\bf Label provenance modeling}: Explicitly encoding expert vs. self-reported reliability addresses core challenge of heterogeneous label quality in multi-source ECG datasets
+\item {\bf Hierarchical supervision}: Dynamic smoothing factors prevent overconfident gradients on noisy labels while preserving sharp supervision on expert-confirmed cases
+\item {\bf Scalability}: Framework aligns with clinical reality—expert labels are scarce but high-quality; self-reported labels are abundant but uncertain
+\item {\bf Performance gap analysis}: Static reliability weights may not capture within-source label heterogeneity; adaptive weighting could improve generalization
+\end{itemize}
 
@@
 %----------------------------------------------------------------------------------------
-%	Limitations, Discussions
+%	FUTURE WORK
 %----------------------------------------------------------------------------------------
 
-\headerbox{Discussions and Limitations}{name=discussion, column=0, below=loss, span=3}{
-% NOT finished
+\headerbox{Future Work}{name=future, column=2, row=4, span=1, below=results}{
+
+{\bf Adaptive Supervision Framework}
 
 \begin{itemize}
-\item The proposed method is relatively effective in digitizing and classifying ECG images concurrently, achieving an acceptable SNR and F1 score.
-This multi-stage framework offers a lightweight and efficient solution to this challenge.
-\vspace{-0.2cm}
-\item There are observable gaps between the SNR metric on the public training data and the hidden validation/test data.
-A possible reason for this discrepancy is the difference in data distribution (format): training data generated using ECG-Image-Kit all follow the standard 3-by-4 format.
-The post-processing step after segmentation is designed to handle this specific format.
-However, the hidden validation/test data may have different formats, e.g.
-additional full-length waveforms.
-\vspace{-0.2cm}
-\item Further improvement directions:
-\vspace{-0.2cm}
-\begin{itemize}
-    \item More effective backbone networks or more advanced architectures, including the latest YOLO series models.
-    \vspace{-0.1cm}
-    \item End-to-end digitization models from the segmented ECG waveform masks or even directly from the ROI can be developed to simplify the pipeline, replacing the current rule-based conversion from pixel coordinates to digitized value.
-    \vspace{-0.1cm}
-    \item Better handling of rotated ECG images to improve the framework's robustness, using oriented object detection models.
-\end{itemize}
+\item {\bf Dynamic reliability}: Learn instance-specific confidence scores vs. static smoothing factors
+\item {\bf Adaptive sampling}: Confidence-aware upsampling responding to model evolution during training
+\item {\bf Data augmentation}: CutMix, SMOTE for positive sample diversification
+\item {\bf Multi-task learning}: Leverage auxiliary arrhythmia labels for enhanced feature representation
+\item {\bf Self-supervised pre-training}: Large-scale unlabeled ECG data for transferable representations
 \end{itemize}
@@
 
-\headerbox{Acknowledgements}{name=acknowledgements, column=0, below=discussion, span=3}{
-% finished
-% \smaller
-We thank professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers to help accomplish this work.
+\headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{
+
+We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers.
+We acknowledge the PhysioNet Challenge organizers and the contributing datasets.
 
@@
 %----------------------------------------------------------------------------------------
-%	link to the GitHub repository
+%	REFERENCES
 %----------------------------------------------------------------------------------------
 
-\headerbox{}{name=foottext, column=0, span=3, below=acknowledgements, textborder=none, headerborder=none,  boxheaderheight=0pt}{
-% finished
+\headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{
+
+\begin{thebibliography}{9}
+\bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
+\bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
+\bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
+\bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
+\bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
+\bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
+\end{thebibliography}
+
+}
+
+%----------------------------------------------------------------------------------------
+%	FOOTER
+%----------------------------------------------------------------------------------------
+
+\headerbox{}{name=foottext, column=0, span=3, below=references, textborder=none, headerborder=none, boxheaderheight=0pt}{
 \hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}

### 2025-08-30 poster.tex
update poster

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 2025 PhysioNet/CinC Challenge Poster
-% Chagas ECG Screening - Team Revenger
+% NIWeek 2014 Poster by T. Reveyrand
+% www.microwave.fr
+% http://www.microwave.fr/LaTeX.html
+% ---------------------------------------
 %
-% Based on baposter template by T. Reveyrand
-% Original template by Brian Amberg (baposter@brian-amberg.de)
-% Downloaded from: http://www.LaTeXTemplates.com
-% License: CC BY-NC-SA 3.0
+% Original template created by:
+% Brian Amberg (baposter@brian-amberg.de)
+%
+% This template has been downloaded from:
+% http://www.LaTeXTemplates.com
+%
+% License:
+% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{textcomp}
+\usepackage{eso-pic}
+\usepackage{enumitem}
 \usepackage{hyperref}
+
+\setlist[itemize]{
+  itemsep=1.5pt,
+  topsep=3pt,
+  parsep=0pt,
+  partopsep=0pt,
+  leftmargin=1em,
+  labelsep=0.4em
+}
+
+\setlength{\abovedisplayskip}{3pt plus 1pt minus 1pt}
+\setlength{\belowdisplayskip}{3pt plus 1pt minus 1pt}
 
@@
 
-% Color definitions (reusing 2024 poster color scheme)
 \definecolor{bordercol}{RGB}{40,40,40} % Border color of content boxes
@@
 \definecolor{jdhblue}{RGB}{2,93,186}
+
 \definecolor{zkblue}{RGB}{88,135,175}
@@
 
+% \usetikzlibrary{shapes, arrows, external, decorations.pathmorphing, backgrounds, positioning, fit, petri, calc, hobby, cd}
+
 \begin{document}
+
+% \background{ % Set the background to an image (background.pdf)
+% \begin{tikzpicture}[remember picture,overlay]
+% \draw (current page.north west)+(-2em,2em) node[anchor=north west]
+% {\includegraphics[height=1.1\textheight]{images/baposter_background.pdf}};
+% \end{tikzpicture}
+% }
+
+% add conference banner
+\AddToShipoutPictureFG*{%
+  \AtPageLowerLeft{%
+    \hspace{0.82em}
+    \raisebox{0.2ex}{\includegraphics[width=0.16\textwidth]{cinc2025-banner.png}}
+  }
+}
 
@@
 headerFontColor=headerfontcol, % Text color for the header text in the content boxes
+% boxColorOne=boxcolor, % Background color for the content in the content boxes
 boxColorOne=zkbackground,
@@
 textborder=rectangle,
+% background=user,
 background=none,
@@
 %
-% TODO: Add logos when available - current paths may not exist
-% \IfFileExists{images/logo_cau_science.png}{\includegraphics[scale=0.401]{images/logo_cau_science.png}}{CAU Logo}
-{{\bf TODO: CAU Logo}} % University/lab logo placeholder
+{\includegraphics[scale=0.401]{logo_cau_science.png}} % University/lab logo
 {
-{\bf \fontsize{18pt}{18pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity}
+{\bf \fontsize{19pt}{19pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
 } % Poster title
@@
 
-$^1${\it College of Science, China Agricultural University}\\
+$^1${\it College of Science, China Agricultural University}\qquad
 $^2${\it Tianjin Medical University} \\
 \vspace{0.2cm}
-{\Large \bf{The George B. Moody PhysioNet Challenge 2025} $\cdot$ \bf{Team Revenger}}
+{\Large \bf{The George B. Moody PhysioNet Challenge 2025}, ~~~\bf{Team Revenger}}
 }
-% \IfFileExists{logo_tmu.jpeg}{\includegraphics[scale=0.101]{logo_tmu.jpeg}}{TMU Logo}
-{{\bf TODO: TMU Logo}} % University logo placeholder
+{\includegraphics[scale=0.101]{logo_tmu.jpeg}}
+
+\newif\ifcoloredtext
+\coloredtexttrue
+\newif\ifboxednn
+\boxednntrue
 
@@
 
-\headerbox{Introduction \& Challenge Context}{name=introduction, column=0, row=0, span=3}{
+\headerbox{Proposed Reliability-Aware Framework}{name=introduction, column=0, row=0, span=3}{
 
@@
 
-\vspace{0.3cm}
 \begin{center}
@@
 \end{center}
-\vspace{0.3cm}
 
@@
 Hierarchical supervision encoding source reliability through stratified label smoothing:
-
-\vspace{0.2cm}
-{\bf Formula:} $\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}$
-\vspace{0.2cm}
-
+\[
+\text{\bf Formula:} ~~ \tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}
+\]
 Where smoothing factor $\varepsilon$ depends on reliability:
@@
 
-\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=2, below=data}{
+\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=1, below=data}{
 
-{\bf Enhanced 1D ResNet with SE Modules \& Global Pooling}
+{\bf Enhanced 1D ResNet with SE Modules}
 
 \begin{center}
-\resizebox{0.95\linewidth}{!}{%
-\begin{tikzpicture}[
-    line width=0.75pt,
-    >={Latex[length=3mm]},
-    node distance=6.4mm,
-    every node/.style={inner sep=2pt},
-    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
-                 align=center, fill=blue!10},
-    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
-                  align=center, fill=orange!12},
-    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
-               align=center, fill=green!12},
-    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
-                 align=center, fill=cyan!10},
-    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
-                 align=center, fill=purple!10},
-    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
-                align=center, fill=red!10},
-    arrow/.style={-{Latex[length=3mm]}, thick},
-]
-
-% Main architecture path
-\node[stem] (input) {Input \\ (12$\times$L)};
-\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};
-\node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1 \\ Ch: $512 \to 768 \to 1024 \to 1280$};
-\node[se, below=of bottleneck] (gse) {Global SE \\ reduction=8};
-\node[pool, below=of gse] (gap) {Global MaxPool};
-\node[head, below=of gap] (mlp) {MLP Head \\ (1280 $\rightarrow$ C=2)};
-\node[output, below=of mlp] (out) {Output Logits};
-
-% Arrows
-\draw[arrow] (input) -- (stem);
-\draw[arrow] (stem) -- (bottleneck);
-\draw[arrow] (bottleneck) -- (gse);
-\draw[arrow] (gse) -- (gap);
-\draw[arrow] (gap) -- (mlp);
-\draw[arrow] (mlp) -- (out);
-
-\end{tikzpicture}
+\resizebox{1.03\linewidth}{!}{%
+  \input{tikz_plots/resnet_nature_comm_bottle_neck}
 }
@@
 \begin{itemize}
-\item {\bf Bottleneck blocks}: 1$\times$1–15$\times$1 convolutions with expansion factor 4, stride 4 downsampling
-\item {\bf Global SE}: Channel attention with reduction ratio 8 for temporal feature recalibration  
-\item {\bf Variable-length inputs}: Global max pooling enables inference on ECGs of any duration
+\item {\bf Bottleneck blocks}: 1-15-1 convolutions, expansion factor 4, stride 4 downsampling
+\item {\bf Global SE}: Channel attention, reduction ratio 8 for temporal feature recalibration  
+\item {\bf Variable-length inputs}: Global MaxPool enables inference on ECGs of any duration
 \end{itemize}
@@
 
-\headerbox{Training \& Optimization}{name=training, column=2, row=2, span=1, below=supervision}{
+\headerbox{Training \& Optimization}{name=training, column=1, row=2, span=1, below=data}{
 
-{\bf Asymmetric Loss \& Optimization Setup}
+% {\bf Asymmetric Loss \& Optimization Setup}
 
@@
 \item Parameters: $(\gamma_{+},\gamma_{-})=(1,4)$, margin $\delta=0.05$
-\item {\bf Optimizer}: AdamW with OneCycle scheduler
-\item {\bf Learning rate}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
+\item {\bf Optimizer}: AdamW
+\item {\bf LR Scheduler}: OneCycle
+\item {\bf LR}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
 \item {\bf Training}: 30 epochs, batch size 128, weight decay $1 \times 10^{-2}$
 \item {\bf Input}: 4,096 samples (uniform crop/center trim)
-\item {\bf Early stopping}: Challenge score on 20\% internal hold-out
+\item {\bf Early stopping}: Challenge score on 20\% internal hold-out subset
 \end{itemize}
@@
 
-\headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{
+% \headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{
 
-We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers.
+% We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers.
 We acknowledge the PhysioNet Challenge organizers and the contributing datasets.
 
-}
+% }
 
@@
 
-\headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{
+% \headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{
 
-\begin{thebibliography}{9}
-\bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
-\bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
-\bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
-\bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
-\bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
-\bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
-\end{thebibliography}
+% \begin{thebibliography}{9}
+% \bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
+% \bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
+% \bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
+% \bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
+% \bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
+% \bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
+% \end{thebibliography}
 
-}
+% }
 
@@
 
-\headerbox{}{name=foottext, column=0, span=3, below=references, textborder=none, headerborder=none, boxheaderheight=0pt}{
+\headerbox{}{name=foottext, column=0, span=3, below=future, textborder=none, headerborder=none, boxheaderheight=0pt}{
 \hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}

### 2025-08-31 contents/methods.tex
fix errors

@@
 \centering
-\begin{tabular}{rlll}
-\toprule
-Dataset & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Chagas rate} & Label provenance \\
-\midrule
-SaMi-Trop   & 1\,631     & 100 \%    & expert-confirmed \\
-CODE-15\%   & 345\,779   & 1.795 \%  & self-reported \\
-PTB-XL      & 21\,799    & 0 \%      & N/A \\
-\bottomrule
-\end{tabular}
+\input{tables/dataset_stats}
 \caption{Dataset statistics and label provenance.
@@
 \label{eq:z_score}
-\tilde{\mathbf{x}} = \frac{\mathbf{x} - \boldsymbol{\mu}_x}{\boldsymbol{\sigma}_x}
+\tilde{\mathbf{x}} = \frac{\mathbf{x} - \boldsymbol{\mu}_{\mathbf{x}}}{\boldsymbol{\sigma}_{\mathbf{x}}}
 \end{equation}
-where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_x$ and $\boldsymbol{\sigma}_x$ are the mean and standard deviation of $\mathbf{x}$, respectively.
+where $\mathbf{x}$ is the original ECG signal, $\boldsymbol{\mu}_{\mathbf{x}}$ and $\boldsymbol{\sigma}_{\mathbf{x}}$ are the mean and standard deviation of $\mathbf{x}$, respectively.
 We excluded ECGs shorter than 1200 samples to ensure inputs contain enough cardiac cycles for stable model analysis.
@@
 \label{eq:label_smoothing}
-\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1},
+\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot {\mathbf{y}} + \frac{\varepsilon}{C} \cdot {\mathbf{1}},
 \end{equation}
@@
 We chose these factors after reviewing hidden validation scores from multiple submissions, as shown in Table~\ref{tab:upsampling_schemes}.
-
 \begin{table}[!htbp]
@@
 \centering
-\begin{tabular}{lcccc}
-\toprule
-\multirow{2}{*}{Dataset} & Upsampling & \multicolumn{2}{c}{Smoothed labels} \\ \cmidrule(lr){3-4}
-& factor & negative & positive \\
-\midrule
-SaMi-Trop & $12$ & N/A           & $[0,\,1]$     \\
-CODE-15\% & $3$ & $[0.7,\,0.3]$ & $[0.3,\,0.7]$ \\
-PTB-XL    & $1$ & $[0.9,\,0.1]$ & N/A           \\
-\bottomrule
-\end{tabular}
+\input{tables/upsampling_schemes}
 \caption{Smoothed labels (computed from Eq.~\ref{eq:label_smoothing}) and upsampling strategies for each dataset.}
@@
 \textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of kernel sizes $1$–$15$–$1$ (pointwise--temporal--pointwise).
-The middle temporal convolution applies a stride of 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4.
-A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
+The middle temporal convolution applies a stride of 4 for downsampling; the two convolutions (kernel size 1) first reduce the number of channels and then expand them with an expansion factor of 4.
+A projection convolution (kernel size 1, stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
 Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$, yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.
@@
 \textbf{Stem and regularization.} A stem Conv1d (kernel size 15, stride 1, 64 channels) with BatchNorm and ReLU precedes the bottleneck stack.
-Within each bottleneck block we apply BatchNorm+ReLU after the first two convolutions and dropout (rate 0.2) after each of those activations.
+Within each bottleneck block, we apply BatchNorm+ReLU after the first two convolutions and dropout (rate 0.2) after each of those activations.
 All convolutions use “same” padding to preserve temporal length before downsampling operations.
 
-Overall, the changes primarily enable variable-length inference and add global channel reweighting with minimal structural overhead.
-The resulting model architecture is illustrated in Fig.~\ref{fig:model}.
+% Overall, the changes primarily enable variable-length inference and add global channel reweighting with minimal structural overhead.
+The overall model architecture is illustrated in Fig.~\ref{fig:model}.
 
@@
 
-We employed an asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to further complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance.
-Let $z$ denote the logits and $p=\sigma(z)$ the predicted probability of the Chagas-positive class, the ASL is defined in Eq.~\ref{eq:asl} with separate focusing parameters for positives and negatives and a clipped negative probability:
+We employed an asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance.
+Let ${\mathbf{z}} = (z_0, z_1)$ denote the logits and $p=\operatorname{softmax}({\mathbf{z}})_1$ the predicted probability of the Chagas-positive class.
+The ASL is defined in Eq.~\ref{eq:asl} with separate focusing parameters for positives and negatives and a clipped negative probability term:
 \begin{equation}
@@
 \end{equation}
-where $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $\delta=0.05$.
-We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle scheduler, weight decay $1\times10^{-2}$).
+where $y$ is the (smoothed) positive-class target probability, $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $m=0.05$.
+We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a OneCycle scheduler, weight decay $1\times10^{-2}$).
 Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric.
-Each training segment is a uniform random crop (or center trim if shorter) of length 4,096 samples.
+Each training segment is a uniform random crop (or center trim if shorter) of length 4096 samples.
 The full implementation, including model construction, data pipeline, and optimization utilities, is based on the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.

### 2025-08-31 contents/results.tex
minor updates
fix errors

@@
 
-The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 170th among 350 submissions.
+The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 187th among 373 submissions.
 The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.
@@
 \centering
-\begin{tabular}{r|r|r|r}
-Training & Validation & Test & Ranking \\\hline
-$0.451 \pm 0.005$ & 0.245 & TBA & 170/350 \\\hline
-\end{tabular}
+\input{tables/official_phase_results}
 \caption{Challenge scores for our submitted entries (team ``Revenger'').

### 2025-08-31 paper_short_in_one.tex
fix errors

@@
 \textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of kernel sizes $1$–$15$–$1$ (pointwise--temporal--pointwise).
-The middle temporal convolution applies a stride of 4 for downsampling; the two 1$\times$1 convolutions first reduce then expand channels with an expansion factor of 4.
-A projection 1$\times$1 convolution (stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
+The middle temporal convolution applies a stride of 4 for downsampling; the two convolutions of kernel size 1 first reduce then expand channels with an expansion factor of 4.
+A projection convolution (kernel size 1, stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
 Across the four blocks, the reduced (bottleneck) channel widths are $128 \to 192 \to 256 \to 320$, yielding expanded output widths $512 \to 768 \to 1024 \to 1280$.

### 2025-08-31 poster.tex
fix errors

@@
 \usepackage{hyperref}
+\usepackage{fix-cm}
 
@@
 {
-{\bf \fontsize{19pt}{19pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
+{\bf \fontsize{17pt}{17pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
 } % Poster title
@@
 
-\headerbox{Data \& Label Provenance}{name=data, column=0, row=1, span=2, below=introduction}{
+\headerbox{Data \& Label Provenance \& Hierarchical Supervision}{name=data, column=0, row=1, span=2, below=introduction}{
 
@@
 \begin{center}
-\begin{tabular}{rlll}
+\begin{tabular}{r|lll|ll}
 \toprule
-Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source \\
+Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source & Upsample factor & Label smooth \\
 \midrule
-SaMi-Trop   & 1,631     & 100.0 \%    & expert-confirmed \\
-CODE-15\%   & 345,779   & 1.8 \%      & self-reported \\
-PTB-XL      & 21,799    & 0.0 \%      & N/A (non-endemic) \\
+SaMi-Trop   & 1,631     & 100 \%    & expert-confirmed  & 12           & 0.0 \\
+CODE-15\%   & 345,779   & 1.795 \%      & self-reported     & 3              & 0.6 \\
+PTB-XL      & 21,799    & 0 \%      & N/A (non-endemic) & $\backslash$ & 0.2 \\
 \bottomrule
@@
 
+\vspace{-3.5ex}
+
 \begin{center}
@@
 \end{center}
+
+\vspace{-2ex}
 

### 2025-08-31 contents/methods.tex
finish poster

@@
 \centering
-\begin{tabular}{ccc}
-\toprule
-\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Challenge score} \\
-\cmidrule(lr){1-2}
-CODE-15\% &  SaMi-Trop & \\
-\midrule
-- & -     & 0.239$^*$ \\
-3 & 7      & 0.212 \\
-3 & 12    & \textbf{0.245} \\
-10 & 120   & 0.210 \\
-6 & 36     & 0.221 \\
-\bottomrule
-\end{tabular}
+\input{tables/upsampling_schemes}
 \caption{Representative upsampling schemes and corresponding Challenge scores on the hidden validation set. The model and training strategies used were the same. “-” indicates no upsampling.\\
-$^*$ obtained during the unofficial phase.
+$^\dagger$ obtained during the unofficial phase.
 }
@@
 \centering
-\input{tables/upsampling_schemes}
+\input{tables/hierarchical_supervision}
 \caption{Smoothed labels (computed from Eq.~\ref{eq:label_smoothing}) and upsampling strategies for each dataset.}
@@
 Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric.
-Each training segment is a uniform random crop (or center trim if shorter) of length 4096 samples.
+Each training segment is a uniform random crop (or center padding if shorter) of length 4096 samples.
 The full implementation, including model construction, data pipeline, and optimization utilities, is based on the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.

### 2025-08-31 poster.tex
finish poster

--- 2025-08-30 poster.tex
@@
 
-\setlength{\abovedisplayskip}{3pt plus 1pt minus 1pt}
-\setlength{\belowdisplayskip}{3pt plus 1pt minus 1pt}
+\setlength{\abovedisplayskip}{1.5pt plus 1pt minus 1pt}
+\setlength{\belowdisplayskip}{1.5pt plus 1pt minus 1pt}
 
@@
   \AtPageLowerLeft{%
-    \hspace{0.82em}
-    \raisebox{0.2ex}{\includegraphics[width=0.16\textwidth]{cinc2025-banner.png}}
+    \hspace{0.77em}
+    \raisebox{0.2ex}{\includegraphics[width=0.147\textwidth]{cinc2025-banner.png}}
   }
@@
 %
-{\includegraphics[scale=0.401]{logo_cau_science.png}} % University/lab logo
+{\includegraphics[scale=0.385]{logo_cau_science.png}} % University/lab logo
 {
-{\bf \fontsize{19pt}{19pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
+{\bf \fontsize{17pt}{17pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
 } % Poster title
@@
 }
-{\includegraphics[scale=0.101]{logo_tmu.jpeg}}
+{\includegraphics[scale=0.097]{logo_tmu.jpeg}}
 
@@
 
-\headerbox{Proposed Reliability-Aware Framework}{name=introduction, column=0, row=0, span=3}{
+\headerbox{Framework Summary \& Key Components}{name=introduction, column=0, row=0, span=3}{
 
 \begin{itemize}
-\item {\bf Team Revenger – PhysioNet Challenge 2025}: ECG-based Chagas cardiomyopathy screening in resource-limited settings
-\item {\bf Challenge objective}: Maximize positive case retrieval under 5\% prevalence constraint for scalable screening
-\item {\bf Key challenge}: Severe class imbalance ($\sim$2\% positives) + expert label scarcity (0.2\% expert-confirmed)
-\item {\bf Our approach}: Reliability-aware hierarchical learning prioritizing expert-confirmed over self-reported labels
+\item We propose a \textbf{reliability-aware hierarchical framework} for ECG-based Chagas screening under scarce and noisy labels.
+The framework comprises three coordinated components: (1) provenance‑stratified label smoothing, (2) moderated source-specific upsampling, and (3) a lightweight variable‑length bottleneck ResNet classifier.
+\item The supervision design assigns sharp targets to expert‑confirmed positives, softened targets to self‑reported samples, and mild smoothing to non‑endemic negatives, while distinct upsampling factors amplify scarce reliable positives without collapsing cohort diversity.
+\item The encoder stacks 4 bottleneck residual blocks with a global squeeze‑and‑excitation module and global max pooling to handle variable-length inputs; training couples reliability‑coded targets with an asymmetric loss to concentrate learning on hard positives amid severe class imbalance.
 \end{itemize}
-
 }
@@
 %----------------------------------------------------------------------------------------
-%	DATA & LABEL PROVENANCE
+%	DATA
 %----------------------------------------------------------------------------------------
 
-\headerbox{Data \& Label Provenance}{name=data, column=0, row=1, span=2, below=introduction}{
-
-Three ECG datasets with heterogeneous label reliability and Chagas prevalence:
-
-\begin{center}
-\begin{tabular}{rlll}
-\toprule
-Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source \\
-\midrule
-SaMi-Trop   & 1,631     & 100.0 \%    & expert-confirmed \\
-CODE-15\%   & 345,779   & 1.8 \%      & self-reported \\
-PTB-XL      & 21,799    & 0.0 \%      & N/A (non-endemic) \\
-\bottomrule
-\end{tabular}
-\end{center}
+\headerbox{Dataset Preparation}{name=data, column=0, row=1, span=1, below=introduction}{
 
 \begin{itemize}
-\item {\bf Preprocessing}: Resampled to 400 Hz, bandpass filtered (0.5–45 Hz), z-score normalized
-\item {\bf Challenge}: Model must learn from heterogeneous label quality and extreme class imbalance
+\item \textbf{Sampling}: All 12-lead ECGs uniformly resampled to 400 Hz.
+\item \textbf{Filtering}: Butterworth bandpass 0.5–45 Hz to suppress baseline wander + high-frequency noise.
+\item \textbf{Normalization}: Per-record z-score
+\begingroup
+\setlength{\abovedisplayskip}{2pt}  % 上间距
+\setlength{\belowdisplayskip}{2pt}  % 下间距
+\[
+\tilde{\mathbf{x}} = \frac{\mathbf{x} - \boldsymbol{\mu}_{\mathbf{x}}}{\boldsymbol{\sigma}_{\mathbf{x}}}
+\]
+\endgroup
+to zero mean, unit variance.
+\item \textbf{Exclusion criteria}: Discard recordings $<1{,}200$ samples ($<3$ s @ 400 Hz) to ensure enough cardiac cycles.
 \end{itemize}
@@
 
-\headerbox{Reliability-Aware Supervision}{name=supervision, column=2, row=1, span=1, below=introduction}{
+\headerbox{Reliability-Aware Supervision}{name=supervision, column=1, row=1, span=2, below=introduction}{
 
-{\bf Label Smoothing \& Upsampling Strategy}
+% Three ECG datasets with heterogeneous label reliability and Chagas prevalence:
 
-Hierarchical supervision encoding source reliability through stratified label smoothing:
-\[
-\text{\bf Formula:} ~~ \tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}
-\]
-Where smoothing factor $\varepsilon$ depends on reliability:
-\begin{itemize}
-\item SaMi positives: $\varepsilon = 0.0$ (max trust)
-\item CODE-15\% samples: $\varepsilon = 0.6$ (uncertainty)  
-\item PTB-XL negatives: $\varepsilon = 0.2$ (mild regularization)
-\end{itemize}
+Hierarchical supervision: source reliability levels (expert > self-report > non-endemic negatives) $\longrightarrow$ calibrated label smoothing ($\varepsilon$) + moderated upsampling.
 
-\vspace{0.3cm}
+\vspace{-1ex}
+% {\smaller[1]
 \begin{center}
-\begin{tabular}{ccc}
+\begin{tabular}{rlllllll}
 \toprule
-\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Score} \\
-\cmidrule(lr){1-2}
-CODE & SaMi & \\
+\multirow{2}{*}{Dataset} & \multirow{2}{*}{Size} & \multirow{2}{*}{Chagas \%} & \multirow{2}{*}{Provenance} & \multirow{2}{*}{Up $\times$} & \multirow{2}{*}{$\varepsilon$} & \multicolumn{2}{c}{Smoothed Targets} \\ \cmidrule(lr){7-8}
+& & & & & & negative & positive \\
 \midrule
-3 & 12    & \textbf{0.245} \\
-3 & 7     & 0.212 \\
-10 & 120   & 0.210 \\
+SaMi-Trop   & 1,631     & 100 \%    & expert-confirmed  & $\times$ 12 & 0.0 & N/A           & $[0,\,1]$     \\
+CODE-15\%   & 345,779   & 1.795 \%  & self-reported     & $\times$ 3  & 0.6 & $[0.7,\,0.3]$ & $[0.3,\,0.7]$ \\
+PTB-XL      & 21,799    & 0 \%      & non-endemic (neg) & $\times$ 1  & 0.2 & $[0.9,\,0.1]$ & N/A           \\
 \bottomrule
@@
 \end{center}
+% }
+\vspace{-1ex}
+
+Label smoothing (binary, $C=2$): $\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot {\mathbf{y}} + \frac{\varepsilon}{C} \cdot {\mathbf{1}}$.
+
+\begin{itemize}
+% \item Reliability levels: expert (sharp, high upsampling) > self-report (soft, moderate) > non-endemic negatives (mild).
+\item Purpose: reduce overconfident gradients for noisier self-reports while preserving expert signal.
+% \item Upsampling balance: (CODE-15\% $\times$3, SaMi-Trop $\times$12) maximized hidden score; aggressive (10,120) overfit / degraded generalization.
+% \item PTB-XL adds negative morphology diversity; mild smoothing (0.2) regularizes the decision boundary.
+% \item Interaction: provenance-aware smoothing complements asymmetric loss (ASL) by encoding prior trust.
+\item Benefit: replaces ad-hoc class weights with structured priors; stabilizes early training variance.
+% \item Limitation: $\varepsilon$ values are manually fixed—do not capture intra-source heterogeneity (future: learn instance reliability).
+\item Complementarity: provenance-based smoothing reduces label noise impact; ASL (asymmetric loss) focuses capacity on hard positives:
+\begingroup
+\setlength{\abovedisplayskip}{2pt}  % 上间距
+\setlength{\belowdisplayskip}{2pt}  % 下间距
+\[
+\operatorname{ASL} = -y \cdot (1-p)^{\gamma_{+}} \log(p) - (1-y) \cdot (p_m)^{\gamma_{-}} \log(1-p_m)
+\]
+\endgroup
+where $p$ is the predicted probability of the positive class, $y$ is the (smoothed) positive-class target probability, $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $m=0.05$.
+\end{itemize}
 
@@
 
-\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=1, below=data}{
+\headerbox{Model Architecture}{name=model, column=0, row=2, span=1, below=data}{
 
 {\bf Enhanced 1D ResNet with SE Modules}
+
+\vspace{-3.5ex}
 
@@
 
+\vspace{-2ex}
+
 \begin{itemize}
+\item {\bf Stem}: Conv1d (kernel 15, stride 1, 64 channels) followed by BN and ReLU, providing initial local morphology modeling.
 \item {\bf Bottleneck blocks}: 1-15-1 convolutions, expansion factor 4, stride 4 downsampling
-\item {\bf Global SE}: Channel attention, reduction ratio 8 for temporal feature recalibration  
-\item {\bf Variable-length inputs}: Global MaxPool enables inference on ECGs of any duration
+\item {\bf Global SE}: Channel attention, reduction ratio 8 for temporal feature recalibration.
+\item {\bf Variable-length inputs}: Global MaxPool enables inference on ECGs of any duration.
+% \item {\bf Classification MLP head}: Hidden FC layer ($1280 \to 1024$) with non-linear activation and dropout (rate 0.2), followed by a final linear layer ($1024 \to 2$) producing class logits.
 \end{itemize}
@@
 %----------------------------------------------------------------------------------------
-%	TRAINING & OPTIMIZATION
+%	UPSAMPLING STRATEGY SELECTION
 %----------------------------------------------------------------------------------------
 
-\headerbox{Training \& Optimization}{name=training, column=1, row=2, span=1, below=data}{
+\headerbox{Upsample Strategy Selection}{name=upsampling, column=1, row=2, span=1, below=supervision}{
+\small
+% \textbf{Goal:} Amplify scarce reliable positives without collapsing inter‑cohort diversity.
 
-% {\bf Asymmetric Loss \& Optimization Setup}
+\begin{center}
+\input{tables/upsampling_schemes}
+\end{center}
+\vspace{-1ex}
+$^\dagger$ obtained during the unofficial phase.
 
 \begin{itemize}
-\item {\bf Asymmetric Loss}: $L = -y(1-p)^{\gamma_{+}} \log(p) - (1-y)(p_m)^{\gamma_{-}} \log(1-p_m)$
-\item Parameters: $(\gamma_{+},\gamma_{-})=(1,4)$, margin $\delta=0.05$
-\item {\bf Optimizer}: AdamW
-\item {\bf LR Scheduler}: OneCycle
-\item {\bf LR}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
-\item {\bf Training}: 30 epochs, batch size 128, weight decay $1 \times 10^{-2}$
-\item {\bf Input}: 4,096 samples (uniform crop/center trim)
-\item {\bf Early stopping}: Challenge score on 20\% internal hold-out subset
+\item Moderate replication outperformed both no upsampling and extreme factors.
+\item Extreme factors increased memorization and reduced hidden generalization.
+% \item PTB-XL (negatives only) kept at ×1 to avoid further skew toward the negative class.
 \end{itemize}
 
+}
+
+%----------------------------------------------------------------------------------------
+%	TRAINING CONFIGURATION
+%----------------------------------------------------------------------------------------
+
+\headerbox{Training Configuration}{name=training, column=2, row=2, span=1, below=supervision}{
+
+\begin{itemize}[leftmargin=8pt,itemsep=2pt,topsep=2pt]
+\item \textbf{Optimizer \& scheduler}: AdamW (weight decay $1\times 10^{-2}$) with OneCycle LR over 30 epochs: base $1\times10^{-4} \rightarrow$ peak $6\times10^{-4}$ (early phase) $\rightarrow$ anneal to $\approx 1\times10^{-6}$.
+% \item \textbf{Batch / epochs / early stop}: Batch size 128; max 30 epochs; early stopping (patience 10) on a fixed 20\% hold-out subset using the Challenge metric.
+\item \textbf{Batch size}: 128.
+\item \textbf{Epochs}: Max 30 epochs.
+\item \textbf{Early stop}: Patience 10 epochs, evaluated on a fixed 20\% hold-out subset using the Challenge metric.
+\item \textbf{Training segments}: Uniform random crop (or center padding if shorter) of 4{,}096 samples.
+\item \textbf{Implementation}: PyTorch + \texttt{torch-ECG} framework
+
+\end{itemize}
 }
@@
 
-\headerbox{Results}{name=results, column=0, row=3, span=3, below=architecture}{
+\headerbox{Results}{name=results, column=1, row=3, span=2, below=upsampling}{
 
-{\bf Challenge Performance \& Analysis}
+% {\bf Challenge Performance \& Analysis}
 
@@
 \end{center}
+\vspace{-1ex}
+The rankings are based on the hidden validation set. Results on the public training data (more specifically, the hold-out subset) are also provided for reference.
+
+}
+
+%----------------------------------------------------------------------------------------
+%	DISCUSSION & Limitations
+%----------------------------------------------------------------------------------------
+
+\headerbox{Discussion \& Limitations}{name=discussion, column=0, row=4, span=3, below=results}{
 
 \begin{itemize}
-\item {\bf Hidden validation score}: 0.245 (Challenge metric: TPR at 5\% prevalence constraint)
-\item {\bf Performance gap}: Internal vs. hidden suggests domain shift or overfitting to public data
-\item {\bf Key insight}: Reliability-aware supervision stabilizes learning under noisy labels more effectively than architectural complexity alone
+\item Our reliability-aware hierarchical framework provides a lightweight, supervision-centric route to Chagas ECG screening under scarce positives and mixed label noise, without relying on heavy architectures or pretraining.
+\item The generalization gap (internal hold-out vs hidden validation) suggests residual distribution shift (cohort composition/prevalence) and under-adaptation of our fixed supervision scheme.
+\item Static supervision limits adaptation: (i) Fixed smoothing factors ($\varepsilon$) capture only coarse provenance, missing intra-source label quality variation; (ii) dataset-level upsampling with fixed multipliers ignores evolving model confidence and per-instance difficulty.
+\item \textbf{Future directions}:
+\begin{itemize}
+\item Adaptive supervision: jointly learn instance-level reliability weights and adjust positive sampling (curriculum/difficulty- or confidence-aware, hard positive mining, etc.) instead of fixed smoothing factors $\varepsilon$ and static upsampling multipliers.
+\item Augmentation \& synthesis: CutMix, mixup variants, temporal warping, and class-conditional synthesis to expand minority morphology diversity.
+\item Multi-task \& pretraining: leverage arrhythmia / morphology labels; self-supervised ECG representation learning before supervised fine-tuning.
+\end{itemize}
 \end{itemize}
@@
 %----------------------------------------------------------------------------------------
-%	DISCUSSION & INSIGHTS
-%----------------------------------------------------------------------------------------
-
-\headerbox{Discussion \& Insights}{name=discussion, column=0, row=4, span=2, below=results}{
-
-{\bf How does the approach provide insight into the Challenge issues?}
-
-\begin{itemize}
-\item {\bf Label provenance modeling}: Explicitly encoding expert vs. self-reported reliability addresses core challenge of heterogeneous label quality in multi-source ECG datasets
-\item {\bf Hierarchical supervision}: Dynamic smoothing factors prevent overconfident gradients on noisy labels while preserving sharp supervision on expert-confirmed cases
-\item {\bf Scalability}: Framework aligns with clinical reality—expert labels are scarce but high-quality; self-reported labels are abundant but uncertain
-\item {\bf Performance gap analysis}: Static reliability weights may not capture within-source label heterogeneity; adaptive weighting could improve generalization
-\end{itemize}
-
-}
-
-%----------------------------------------------------------------------------------------
-%	FUTURE WORK
-%----------------------------------------------------------------------------------------
-
-\headerbox{Future Work}{name=future, column=2, row=4, span=1, below=results}{
-
-{\bf Adaptive Supervision Framework}
-
-\begin{itemize}
-\item {\bf Dynamic reliability}: Learn instance-specific confidence scores vs. static smoothing factors
-\item {\bf Adaptive sampling}: Confidence-aware upsampling responding to model evolution during training
-\item {\bf Data augmentation}: CutMix, SMOTE for positive sample diversification
-\item {\bf Multi-task learning}: Leverage auxiliary arrhythmia labels for enhanced feature representation
-\item {\bf Self-supervised pre-training}: Large-scale unlabeled ECG data for transferable representations
-\end{itemize}
-
-}
-
-%----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-% \headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{
-
-% We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers.
-We acknowledge the PhysioNet Challenge organizers and the contributing datasets.
-
-% }
-
-%----------------------------------------------------------------------------------------
-%	REFERENCES
-%----------------------------------------------------------------------------------------
-
-% \headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{
-
-% \begin{thebibliography}{9}
-% \bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
-% \bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
-% \bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
-% \bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
-% \bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
-% \bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
-% \end{thebibliography}
-
-% }
-
-%----------------------------------------------------------------------------------------
 %	FOOTER
@@
 
-\headerbox{}{name=foottext, column=0, span=3, below=future, textborder=none, headerborder=none, boxheaderheight=0pt}{
+\headerbox{}{name=foottext, column=0, span=3, below=discussion, textborder=none, headerborder=none, boxheaderheight=0pt}{
 \hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}

### 2025-08-31 paper_short_in_one.tex
update the auto-generated paper_short_in_one.tex file

@@
 
-Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 179~/~364).
+Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 187~/~373).
 In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
@@
 \toprule
-\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Challenge score} \\
-\cmidrule(lr){1-2}
-CODE-15\% &  SaMi-Trop & \\
-\midrule
-- & -     & 0.239$^*$ \\
+\multicolumn{2}{c}{Upsample factor} & \multirow{2}{*}{Challenge score} \\ \cmidrule(lr){1-2}
+CODE-15\% & SaMi-Trop               &                                  \\ \midrule
+-         & -                       & 0.239$^\dagger$                        \\
 3         & 7                       & 0.212                            \\
@@
 \caption{Representative upsampling schemes and corresponding Challenge scores on the hidden validation set. The model and training strategies used were the same. “-” indicates no upsampling.\\
-$^*$ obtained during the unofficial phase.
+$^\dagger$ obtained during the unofficial phase.
 }
@@
 \textbf{(1) Bottleneck residual blocks.} We replace basic ResNet blocks with bottleneck blocks of kernel sizes $1$–$15$–$1$ (pointwise--temporal--pointwise).
-The middle temporal convolution applies a stride of 4 for downsampling; the two convolutions of kernel size 1 first reduce then expand channels with an expansion factor of 4.
+The middle temporal convolution applies a stride of 4 for downsampling; the two convolutions (kernel size 1) first reduce the number of channels and then expand them with an expansion factor of 4.
 A projection convolution (kernel size 1, stride 4) is used in the residual branch whenever temporal resolution or channel width changes.
@@
 \end{equation}
-where $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $\delta=0.05$.
-We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a One-Cycle scheduler, weight decay $1\times10^{-2}$).
+where $y$ is the (smoothed) positive-class target probability, $p_m = \max(p - m, 0),$ $(\gamma_{+},\gamma_{-})=(1,4)$ and margin $m=0.05$.
+We train for 30 epochs with batch size 128 using the AdamW optimizer (initial learning rate $1\times10^{-4}$, peak $6\times10^{-4}$ under a OneCycle scheduler, weight decay $1\times10^{-2}$).
 Early stopping (patience 10 epochs, monitored on a fixed 20\% internal hold-out subset) selects the final model via the Challenge metric.
-Each training segment is a uniform random crop (or center trim if shorter) of length 4,096 samples.
+Each training segment is a uniform random crop (or center padding if shorter) of length 4096 samples.
 The full implementation, including model construction, data pipeline, and optimization utilities, is based on the \texttt{torch-ECG} framework \cite{torch_ecg_paper}.
@@
 \begin{tabular}{r|r|r|r}
-Training & Validation & Test & Ranking \\\hline
-$0.451 \pm 0.005$ & 0.245 & TBA & 179~/~364 \\\hline
+Training          & Validation & Test & Ranking   \\ \hline
+$0.451 \pm 0.005$ & 0.245      & TBA  & 187~/~373 \\ \hline
 \end{tabular}

### 2025-09-25 contents/abstract.tex
fix errors
update final test results

@@
 
-Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 179~/~364).
-In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
+Results: On the hidden validation set, our method received a Challenge score of 0.163 (rank 32~/~40). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
 
-Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.
+Conclusion: The proposed method demonstrates effective performance for ECG-based Chagas screening, highlighting its potential for improving detection accuracy and reliability in resource-limited scenarios.
 

### 2025-09-25 contents/discussions.tex
update final test results

@@
 
-The hidden validation Challenge score presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement.
+The Challenge scores presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement.
 The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision.

### 2025-09-25 poster.tex
update final test results

@@
 \begin{tabular}{r|r|r|r}
-Internal hold-out (mean±std) & Hidden validation & Rank & Test \\
+Internal hold-out (mean±std) & Hidden validation & Test & Rank \\
 \hline
-$0.451 \pm 0.005$ & 0.245 & 179/364 & TBA \\
+$0.451 \pm 0.005$ & 0.245 & 0.163 & 32/40 \\
 \hline
@@
 \vspace{-1ex}
-The rankings are based on the hidden validation set. Results on the public training data (more specifically, the hold-out subset) are also provided for reference.
+The rankings are based on the hidden test set. Results on the public training data (more specifically, the hold-out subset) are also provided for reference.
 

### 2025-09-26 paper_short_in_one.tex
update auto-generated file paper_short_in_one.tex

@@
 
-Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 187~/~373).
-In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
+Results: On the hidden validation set, our method received a Challenge score of 0.163 (rank 32~/~40). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
 
-Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.
+Conclusion: The proposed method demonstrates effective performance for ECG-based Chagas screening, highlighting its potential for improving detection accuracy and reliability in resource-limited scenarios.
 
@@
 
-The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 187th among 373 submissions.
+The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 teams eligible for rankings.
 The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.
@@
 \centering
+% \input{tables/official_phase_results}
 \begin{tabular}{r|r|r|r}
 Training          & Validation & Test & Ranking   \\ \hline
-$0.451 \pm 0.005$ & 0.245      & TBA  & 187~/~373 \\ \hline
+$0.451 \pm 0.005$ & 0.245      & 0.163  & 32~/~40 \\ \hline
 \end{tabular}
+
 \caption{Challenge scores for our submitted entries (team ``Revenger'').

### 2025-09-26 compile.py
fix compiled file name

@@ -45,20 +45,20 @@ def execute_cmd(cmd: Union[str, List[str]], raise_error: bool = True) -> Tuple[i
     debug_stdout = collections.deque(maxlen=1000)
     # print("\n" + "*" * 10 + "  execute_cmd starts  " + "*" * 10 + "\n")
     while 1:
-        line = s.stdout.readline().decode("utf-8", errors="replace")
+        line = s.stdout.readline().decode("utf-8", errors="replace")  # type: ignore
         if line.rstrip():
             debug_stdout.append(line)
             print(line)
         exitcode = s.poll()
         if exitcode is not None:
-            for line in s.stdout:
+            for line in s.stdout:  # type: ignore
                 debug_stdout.append(line.decode("utf-8", errors="replace"))
             if exitcode is not None and exitcode != 0:
                 error_msg = " ".join(cmd) if not isinstance(cmd, str) else cmd
                 error_msg += "\n"
                 error_msg += "".join(debug_stdout)
                 s.communicate()
-                s.stdout.close()
+                s.stdout.close()  # type: ignore
                 print("\n" + "*" * 10 + "  execute_cmd failed  " + "*" * 10 + "\n")
                 if raise_error:
                     raise subprocess.CalledProcessError(exitcode, error_msg)
@@ -68,7 +68,7 @@ def execute_cmd(cmd: Union[str, List[str]], raise_error: bool = True) -> Tuple[i
             else:
                 break
     s.communicate()
-    s.stdout.close()
+    s.stdout.close()  # type: ignore
     output_msg = list(debug_stdout)
 
     # print("\n" + "*" * 10 + "  execute_cmd succeeded  " + "*" * 10 + "\n")
@@ -118,7 +118,7 @@ def main():
     if output_file_name is not None:
         backup_pdf_file = build_dir / output_file_name
     elif tex_entry_file.stem == main_tex_file.stem and handout:
-        backup_pdf_file = build_dir / f"CinC2024-Paper-{suffix}.pdf"
+        backup_pdf_file = build_dir / f"CinC2025-Paper-{suffix}.pdf"
     else:
         backup_pdf_file = build_dir / f"{tex_entry_file.stem}.pdf"
     shutil.copy(generated_pdf_file, backup_pdf_file)

### 2025-10-08 contents/abstract.tex
revise the final paper

@@
 % almost finished
-
-% --------------------------------------------------
-% Unofficial phase version:
-
-% Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B.
-Moody PhysioNet Challenge 2025.
-
-% Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance.
-We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive).
-The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported.
-We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones.
-Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability).
-Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence.
-A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.
-
-% Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.
-
-% Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
-% --------------------------------------------------
 
@@
 
-Results: On the hidden validation set, our method received a Challenge score of 0.163 (rank 32~/~40). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.
+Results: On the official hidden test set, our method received a Challenge score of 0.163, ranking 32nd of 40 eligible teams.
 

### 2025-10-08 contents/discussions.tex
revise the final paper

@@
 
-The Challenge scores presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement.
+The Challenge scores presented in Table~\ref{tab:scores} indicate that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement.
 The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision.
@@
 
-However, the performance gap between our internal hold-out subset and the hidden validation set suggests two primary limitations.
+% However, the performance gap between our internal hold-out subset and the hidden test set suggests two primary limitations.
 First, the reliability weights (smoothing factors) were pre-defined based on label provenance rather than learned from data.
@@
 
-Future research directions will primarily focus on the development of a self-adaptive supervision framework.
-This includes dynamic weighting schemes for learning instance-specific reliability scores, moving beyond static smoothing factors; and adaptive sampling strategies that respond to the model's evolving confidence during training, offering a promising alternative to fixed upsampling factors.
+However, the performance gap between our internal hold-out subset and the hidden test set indicates limitations in our method's generalization capability.
+This is also reflected in the absolute performance, where our Challenge score is substantially behind those of the top-performing teams (e.g., 0.323, 0.283, 0.280).
+The leading approaches generally leveraged some form of large-scale representation learning, such as pre-trained Vision Transformer foundation models or self-supervised learning on extensive ECG datasets.
+These strategies focus on building robust, general-purpose feature extractors.
+In contrast, our work prioritized a distinct niche by designing a resource-efficient pipeline that explicitly addresses the challenges of label noise and scarcity through reliability-aware smoothing and asymmetric loss, without relying on massive pretraining.
+While this choice enhances practicality and stability under noisy supervision, it appears that the representational capacity of our directly-trained model is ultimately lower, limiting its ability to generalize as effectively as the foundation-model-based approaches.
+Furthermore, our static assignment of reliability weights, which cannot adapt to instance-specific label quality, represents another limitation compared to more dynamic or learned weighting schemes.
+
+% Future research directions will primarily focus on developing a self-adaptive supervision framework.
+This includes dynamic weighting schemes for learning instance-specific reliability scores, moving beyond static smoothing factors, and adaptive sampling strategies that respond to the model's evolving confidence during training, offering a promising alternative to fixed upsampling factors.
 Data augmentation techniques, such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE}, could be applied to further expand and diversify the positive samples, thereby enhancing the model's robustness against overfitting and improving generalization to underrepresented patterns.
@@
 Exploring self-supervised pre-training on large-scale unlabeled ECG data also represents a promising direction to learn more transferable representations before fine-tuning on the target task.
+
+Building upon these insights, future research will focus on bridging the generalization gap while retaining our focus on learning under weak supervision.
+A primary direction is the self-adaptive supervision framework.
+This includes dynamic weighting schemes, moving beyond our current static factors, and adaptive sampling strategies that respond to the model's evolving confidence during training.
+To further improve robustness and handle class imbalance, advanced data augmentation techniques such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE} will be explored to diversify the limited positive samples, with a particular focus on ECG-specific transformations like lead-wise masking.
+Furthermore, inspired by the success of representation learning, we plan to explore self-supervised pre-training on large-scale unlabeled ECG data as a pivotal step to learn more transferable representations before fine-tuning.
+This direction, while computationally more demanding, addresses a key limitation identified in our current work.
+Additionally, a multi-task learning framework leveraging auxiliary arrhythmia labels could be integrated to impose clinically meaningful constraints and enhance the feature representation for the primary Chagas screening task.

### 2025-10-08 contents/methods.tex
revise the final paper

@@
 \centering
+\adjustbox{width=0.70\linewidth}{
 \input{tikz_plots/resnet_nature_comm_bottle_neck}
+}
 \caption{Model architecture.
-Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
+Left: overall network: a stem (Conv1d, kernel size 15, 64 output channels, Batch Normalization, ReLU) followed by four bottleneck residual blocks, a global SE module, global max pooling, and an MLP head producing $C = 2$ logits.
 Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
-Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
+Right: internal bottleneck structure.
 The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path.
@@
 
-We employed an asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance.
-Let ${\mathbf{z}} = (z_0, z_1)$ denote the logits and $p=\operatorname{softmax}({\mathbf{z}})_1$ the predicted probability of the Chagas-positive class.
+We employed asymmetric loss (ASL) \cite{ridnik2021asymmetric_loss} to complement the reliability-aware label smoothing strategy, jointly addressing the challenges of severe class imbalance.
+Let ${\mathbf{z}} = (z_0, z_1)$ denote the logits and $p=\operatorname{softmax}({\mathbf{z}})_1$ the predicted probability of the positive class.
 The ASL is defined in Eq.~\ref{eq:asl} with separate focusing parameters for positives and negatives and a clipped negative probability term:

### 2025-10-08 contents/results.tex
update final test results
minor updates
revise the final paper

--- 2025-03-02 contents/results.tex
@@
 
-% NOT  finished
+% almost finished
 
-to write
+The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 eligible teams.
+This score and ranking, along with extra scores on the internal hold-out of the public training data, and on the hidden validation set, are summarized in Table~\ref{tab:scores}.
+
+\begin{table}[!htp]
+\centering
+% \input{tables/official_phase_results}
+\input{tables/final_results}
+\caption{Challenge scores for our submitted entries (team ``Revenger'').
+Training: internal hold-out mean $\pm$ std over repeated runs.
+Validation: best among 10 validation submissions.
+Test: the unique test submission.
+Ranking: position on the hidden test leaderboard.}
+\label{tab:scores}
+\end{table}

### 2025-10-08 poster.tex
minor updates
revise the final paper

@@
 
-\vspace{-3.5ex}
+\vspace{-2.5ex}
 
@@
 
-\vspace{-2ex}
+\vspace{-0.5ex}
 
 \begin{itemize}
-\item {\bf Stem}: Conv1d (kernel 15, stride 1, 64 channels) followed by BN and ReLU, providing initial local morphology modeling.
+\item {\bf Stem}: Conv1d (kernel 15, stride 1, 64 output channels) followed by BN and ReLU, providing initial local morphology modeling.
 \item {\bf Bottleneck blocks}: 1-15-1 convolutions, expansion factor 4, stride 4 downsampling
@@
 \begin{tabular}{r|r|r|r}
-Internal hold-out (mean±std) & Hidden validation & Test & Rank \\
+Internal hold-out (mean±std) & Hidden validation & Test & Ranking \\
 \hline
-$0.451 \pm 0.005$ & 0.245 & 0.163 & 32/40 \\
+$0.451 \pm 0.005$ & 0.245 & 0.163 & 32~/~40 \\
 \hline

### 2025-10-08 paper_short_in_one.tex
update the auto-generated paper_short_in_one.tex file

@@
 
+\usepackage{adjustbox}
+
 % \tikzstyle{smallcircleblock} = [circle, draw, text width = 0.7em, text centered]
@@
 
-% --------------------------------------------------
-% Unofficial phase version:
-
-% Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B.
-Moody PhysioNet Challenge 2025.
-
-% Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance.
-We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive).
-The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported.
-We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones.
-Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability).
-Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence.
-A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.
-
-% Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.
-
-% Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
-% --------------------------------------------------
-
 Aim: We present a reliability-aware hierarchical learning framework for ECG-based Chagas cardiomyopathy screening in the George B.
@@
 Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B.
-Moody PhysioNet Challenge \cite{goldberger2000physionet, cinc2025}.
+Moody PhysioNet Challenge \cite{goldberger2000physionet, 2025ChallengeCinC, 2025ChallengePreprint}.
 Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.
@@
 \centering
+\adjustbox{width=0.70\linewidth}{
 \begin{tikzpicture}[
@@
 \node[stem] (input) {Input \\ (12$\times$L)};
-\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};
+\node[stem, below=of input] (stem) {Stem \\ Conv ks=15, 64 Ch \\ BN + ReLU};
 
@@
 % Anchor for expansion (to the right of overall bottleneck block)
-\coordinate (expandAnchor) at ($(input.east)+(45mm,0)$);
+\coordinate (expandAnchor) at ($(input.east)+(50mm,0.2)$);
 
@@
 
+}
 \caption{Model architecture.
-Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits.
+Left: overall network: a stem (Conv1d, kernel size 15, 64 output channels, Batch Normalization, ReLU) followed by four bottleneck residual blocks, a global SE module, global max pooling, and an MLP head producing $C = 2$ logits.
 Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
-Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise).
+Right: internal bottleneck structure.
 The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path.
@@
 
-The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 teams eligible for rankings.
-The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.
+The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 eligible teams.
+This score and ranking, along with extra scores on the internal hold-out of the public training data, and on the hidden validation set, are summarized in Table~\ref{tab:scores}.
 
@@
 \begin{tabular}{r|r|r|r}
-Training          & Validation & Test & Ranking   \\ \hline
-$0.451 \pm 0.005$ & 0.245      & 0.163  & 32~/~40 \\ \hline
+Training          & Validation & \textbf{Test}  & \textbf{Ranking} \\ \hline
+$0.451 \pm 0.005$ & 0.245      & \textbf{0.163} & \textbf{32~/~40} \\ \hline
 \end{tabular}
@@
 Validation: best among 10 validation submissions.
-Test: to be announced.
-Ranking: position on the hidden validation leaderboard.}
+Test: the unique test submission.
+Ranking: position on the hidden test leaderboard.}
 \label{tab:scores}
@@
 Exploring self-supervised pre-training on large-scale unlabeled ECG data also represents a promising direction to learn more transferable representations before fine-tuning on the target task.
+
+Building upon these insights, future research will focus on bridging the generalization gap while retaining our focus on learning under weak supervision.
+A primary direction is the self-adaptive supervision framework.
+This includes dynamic weighting schemes, moving beyond our current static factors, and adaptive sampling strategies that respond to the model's evolving confidence during training.
+To further improve robustness and handle class imbalance, advanced data augmentation techniques such as CutMix \cite{yun2019cutmix} and SMOTE \cite{Chawla_2002_SMOTE} will be explored to diversify the limited positive samples, with a particular focus on ECG-specific transformations like lead-wise masking.
+Furthermore, inspired by the success of representation learning, we plan to explore self-supervised pre-training on large-scale unlabeled ECG data as a pivotal step to learn more transferable representations before fine-tuning.
+This direction, while computationally more demanding, addresses a key limitation identified in our current work.
+Additionally, a multi-task learning framework leveraging auxiliary arrhythmia labels could be integrated to impose clinically meaningful constraints and enhance the feature representation for the primary Chagas screening task.
 

### 2025-10-31 preamble.tex
add aggregated file paper_short_in_one.tex
revise the final paper
update recent review opinion and make corr. changes.

@@
 
+% --- unify spacing between floats and text (single-/double-column) ---
+\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}   % text <-> single-column floats (table/figure)
+\setlength{\intextsep}{6pt plus 2pt minus 2pt}      % inline [h] floats
+\setlength{\floatsep}{6pt plus 2pt minus 2pt}       % float <-> float (single-column)
+
+\setlength{\dbltextfloatsep}{6pt plus 2pt minus 2pt} % text <-> double-column floats (figure*)
+\setlength{\dblfloatsep}{6pt plus 2pt minus 2pt}     % float <-> float (double-column)
+
+% --- caption spacing for tables only ---
+\captionsetup[table]{aboveskip=6pt, belowskip=0pt}
+
 \newenvironment{indentedquote}[1]%
@@
 {\endlist}
+
+\newcommand\wordcount{\input{|"texcount -inc -sum -0 -utf8 -ch -template={SUM} \currfilepath"}}

### 2025-10-31 paper_short_in_one.tex
update the auto-generated paper_short_in_one.tex file

@@
 \boxednntrue
+
+% --- unify spacing between floats and text (single-/double-column) ---
+\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}   % text <-> single-column floats (table/figure)
+\setlength{\intextsep}{6pt plus 2pt minus 2pt}      % inline [h] floats
+\setlength{\floatsep}{6pt plus 2pt minus 2pt}       % float <-> float (single-column)
+
+\setlength{\dbltextfloatsep}{6pt plus 2pt minus 2pt} % text <-> double-column floats (figure*)
+\setlength{\dblfloatsep}{6pt plus 2pt minus 2pt}     % float <-> float (double-column)
+
+% --- caption spacing for tables only ---
+\captionsetup[table]{aboveskip=6pt, belowskip=0pt}
 
@@
 \centering
-\adjustbox{width=0.70\linewidth}{
+\adjustbox{width=0.73\linewidth}{
 \begin{tikzpicture}[
@@
 
-\begin{table}[!htp]
+% \begin{table}[!htp]
+\begin{table}[!h]
 \centering
@@
 
-\textbf{Stem and regularization.} A stem Conv1d (kernel size 15, stride 1, 64 channels) with BatchNorm and ReLU precedes the bottleneck stack.
+\textbf{(4) Stem and regularization.} A stem Conv1d (kernel size 15, stride 1, 64 channels) with BatchNorm and ReLU precedes the bottleneck stack.
 Within each bottleneck block, we apply BatchNorm+ReLU after the first two convolutions and dropout (rate 0.2) after each of those activations.
